### 2024-11-27 paper/paper.qmd
updates scripts, LLM usage, and data/intro section of paper

---
title: "Which Factors are Associated with Wikipedia Relevancy?"
subtitle: "An Analysis of Notable People on Wikipedia"
author: 
  - Parth Samant
thanks: "Code and data are available at: [https://github.com/samantparth/Wikipedia-Historical-Prominence-Trends](https://github.com/samantparth/Wikipedia-Historical-Prominence-Trends)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(modelsummary)
library(readr)
library(arrow)
library(ggplot2)
library(knitr)

cleaned_data <- read_parquet(here::here("data/analysis_data/analysis_data.parquet"))

```

# Introduction

Overview paragraph

Understanding prominence of individuals on offers a way to quantify the societal impact of individuals through time. By using a dataset of notable people on Wikipedia from 3500 BCE to 2018 AD, this paper uses a bayesian linear model to identify certain factors associated with prominence. Some of the factors focused on include nationality, gender, occupation, and the number of years since the individuals birth. Analysing potential trends allows us to evaluate potential patterns and bias in one's relevance.

Estimand paragraph

The estimating (or what we are estimating) is the prominence of their Wikipedia biography based on percentile. "Prominence" of a biography is determined using multiple metrics, such as the average amount of views per year, the total word count, and the number of Wikipedia editions.

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

## Overview

All data analysis was done through the statistical programming language R [@citeR] with the packages `tidyverse`[@tidyverse], `rstanarm` [@rstanarm], `modelsummary` [@modelsummary], `arrow`[@arrow], `readr`[@readr], `httr`[@httr], `R.utils`[@R.utils], `knitr`[@knitr] and `ggplot2` [@ggplot].

## Measurement [@sec-measurement]

Wikipedia is an online encyclopedia that provides information on numerous subjects, including the lives of those who are relatively well-known.Thus, the data comes from a research study [@notablepeople] that aims to build a cross-verified database of 'notable people' who have ever lived by using information from Wikipedia. Those with a Wikipedia article are considered "notable", as the overwhelming majority of people who have ever lived do not have one. Additionally, this dataset of notable people is very large (with hundreds of thousands of entries), reflecting the large amount of notable people that are written about on Wikipedia.

This data was obtained using the Wikidata universe (which provides data on Wikipedia), where they used the "instance of humans" category to select for a sample of notable individuals. Many potential obstacles (including identifying non-humans vs humans or multiple biographies) were controlled for when this dataset was made.

Based on the information provided in those Wikipedia articles, the study was also able to identify characteristics of these people. Some of these factors include nationality, occupation, and age.

Furthermore, the researchers constructed many variables including `ranking_visib_5criteria`, which ranks the prominence of an individual on Wikipedia. The ranking is dependent on these 5 metrics :

- the number of different editions;
- the number of non-missing items for birth date, gender, and domain of influence;
- the total number of words for their article;
- average yearly number of viewers from 2015 to 2018;
- number of external links (such as sources and references) from Wikidata.

## Data Cleaning and Variables

This dataset was cleaned by first mutating some variables, selecting/renaming variables of interest, and filtering out rows with missing information, randomly selecting 10,000 entries from the dataset. The variables selected are mentioned later on in this section.

Since this paper focuses on predicting historical prominence, I chose variables which I thought could be associated with the outcome variable (`percentile_rank`).

Outcome Variable:

- `**percentile_rank**`: a transformation of the variable `ranking_visib_5criteria` (as mentioned in @sec-measurement). This indicates the percentile associated with the notability ranking. A higher percentile indicates they were a more notable person.

Predictor Variables:

- `**subregion**`: the UN subregion corresponding to where they were from. This is simply a renaming of the variable `un_subregion`.

- `**years_since_birth**`: the number number of years that have passed since their birth. If they are alive, this is simple their age.

- `**time_period**`: The time period that they were born in.

- `**gender**`: The reported gender of the individual (either male or female).

- `**occupation**`: The primary field/occupation that the individual is known for.

## Analysis of Variables

### Subregion

In @fig-subregion-counts, we can visualize the distribution of each geographic sub region.

```{r}

#| label: fig-subregion-counts
#| fig-cap: Proportion of Notable People by Subregion
#| echo: false

summary_table_subregion <- cleaned_data |>
  group_by(subregion) |>
  summarize(Count = n()/nrow(cleaned_data)) |>
  arrange(desc(Count))

summary_table_subregion |>
 kable()
```
@fig-subregion-counts provides a detailed view of the prevalence of notable people by subregion. Interestingly, subregions that are a part of the Western world tend to be over-represented in terms of notable people.  In fact, the difference is so stark that the most well-represented region (Western Europe) has nearly 100x the representation of notable people than West Africa.

There could be many explanations for this, such as how Western nations tend to have more global cultural dominance (and thus more 'notable people').

### time_period/years_since_birth

These are two variables that are directly associated with each other, since the time period of ones life is directly a result of the number of years since their birth.

However, a notable feature of `years_since_birth` (and thus `time_period`) is the distribution as shown in @fig-years_since_birth.
```{r}
#| label: fig-years_since_birth
#| fig-cap: Distribution of Notable Individuals by Years Since Birth
#| echo: false

hist(cleaned_data$years_since_birth, xlab = "Years Since Birth",main = NULL)

```

From @fig-years_since_birth, we can see that the overwhelming majority of documented notable people on Wikipedia tend to be born in the past 500 or so years. This makes sense, as retrieving information on individuals that lived a longer time ago is more difficult. Future plots and analyses will thus use the logarithm of this variable to have a more detailed view on its impact.

### Time Period and Subregion

Different regions had different levels of cultural relevance/dominance depending on the time period. Because of this fact, it may be possible that the prevalence of subregions can heavily depend on the number of years since their birth.

In @fig-time-subregion, we can see this relationship quite clearly. Note that the proportions are out of the top 5 most popular subregions, rather than every subregion. This was done to ensure readability.

```{r}
#| label: fig-time-subregion
#| fig-cap: Top 5 Subregions by Time Period
#| echo: false

# Count occurrences of subregion by time_period
cleaned_data_filtered <- cleaned_data |>
  count(time_period, subregion)

# Filter to the top 5 subregions by count for each time_period
top5_subregions <- cleaned_data_filtered |>
  group_by(time_period) 
  slice_max(order_by = n, n = 5) |>
  ungroup()

# Recalculate proportions within the filtered top 5 data
cleaned_data_top5 <- top5_subregions %>%
  group_by(time_period) %>%
  mutate(proportion = n / sum(n)) %>%  # Recalculate proportions after filtering
  ungroup()

# creating graph
ggplot(data = cleaned_data_top5, aes(x = time_period, y = proportion, fill = subregion)) +
  geom_bar(stat = "identity", position = "stack") + 
  theme_minimal() +
  labs(
    x = "Time Period",
    y = "Proportion",
    fill = "Subregion"
  ) +
  scale_fill_brewer(palette = "Set3") + 
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1), 
    legend.position = "right"  
  )
```
From @fig-time-subregion, we can confirm the relationship between the time period and subregion - that the prevalency of notable individuals heavily changes depending on the time period in question. The most notable example is the decrease in prevalence for Southern Europe/East Asia and the subsequent rise of Northern America (i.e., the USA and Canada) and Western Europe.

As mentioned above, this confirms the phenomenon of how different subregions have different levels of influence depending on the time period. This graph especially highlights the rise of notable people in Western Europe as well as its descendant countries.

### Gender and Occupation

The remaining variables, gender and occupation, may also show some sort of trend (since ones field of work is often quite gendered). This relationship is shown in @tbl-gender-occupation, which shows ones occupation (or more specifically, what they are known for).

```{r}
#| label: tbl-gender-occupation
#| fig-cap: Occupations of Notable People by Gender
#| echo: false

summary_table_occupation <- cleaned_data |>
  group_by(occupation) |>
  summarize(
    Count = n(),
    female_count = sum(gender=="Female"),
    male_count = sum(gender=="Male"),
    proportion_female = female_count/Count,
    proportion_male = male_count/Count) |>
  arrange(desc(proportion_female))

summary_table_occupation |>
 select(occupation, proportion_female,proportion_male) |>
  kable(digits=2)
```
@tbl-gender-occupation shows that those of nobility (often by being born in a high social rank) tend to have a higher proportion of females, where other occupations - such as the military - tend to have a higher proportion of males.

Interestingly, even the most female-dominated occupation (nobility) is still roughly 2/3rds men. This reflects a clear bias in people that are considered 'notable': men are very much over-represented in every occupation (and in this dataset, as a result).

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2024-11-27 scripts/02-download_data.R

@@ -1,11 +1,10 @@
 #### Preamble ####
-<<<<<<< HEAD
 # Purpose: Downloads and saves the data from Notable People Wikipedia Dataset
 # Author: Parth Samant
 # Date: 25 November 2024
 # Contact: parth.samant@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: Make sure tidyverse, readr, httr, R.utils have been downloaded
+# Pre-requisites: Make sure tidyverse, readr, httr, R.utils libraries have been downloaded
 # Any other information needed? None
 
 

### 2024-11-27 scripts/03-clean_data.R

@@ -1,24 +1,54 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 6 April 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Cleans Raw Dataset, Selects for Notable Variables, Adds Standardized Popularity Variable
+# Author: Parth Samant
+# Date: 25 November 2024
+# Contact: parth.samant@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: Make sure tidyverse, readr, and arrow libraries have been downloaded
+# Any other information needed? None
+
 
 #### Workspace setup ####
 library(tidyverse)
 library(readr)
+library(arrow)
 
 #### Clean data ####
-raw_data <- read_csv("data/raw_data.csv")
+raw_data <- read_csv("data/raw_data/raw_data.csv")
+
+# To make data reproducible
+set.seed(200)
 
 
+#Selecting for relevant columns, as well as making a couple new ones
 cleaned_data <- raw_data |>
-  sample_n(2000)
+  mutate(
+    percentile_rank = percent_rank(-ranking_visib_5criteria),
+    years_since_birth = 2024-birth
+    ) |>
+  select(name, years_since_birth, gender, level2_main_occ, bigperiod_birth_graph_b, un_subregion, percentile_rank) |> 
+  filter(if_all(c(years_since_birth, gender, level2_main_occ, bigperiod_birth_graph_b, un_subregion, percentile_rank), ~ !is.na(.))) |>
+  sample_n(10000, replace = FALSE) |>
+  rename(
+    occupation = level2_main_occ,
+    time_period = bigperiod_birth_graph_b,
+    subregion = un_subregion
+  ) |>
+  mutate(
+    time_period = 
+      case_match(
+        time_period,
+        "5.Contemporary period 1901-2020AD" ~ "5. 1901-2020AD",
+        "4.Mid Modern Period 1751-1900AD" ~ "4. 1751-1900AD",
+        "3.Early Modern Period 1501-1750AD" ~ "3. 1501-1750AD",
+        "2.Post-Classical History 501-1500AD" ~ "2. 501-1500AD",
[…]

### 2024-11-27 scripts/06-model_data.R

@@ -11,27 +11,40 @@
 #### Workspace setup ####
 library(tidyverse)
 library(rstanarm)
+library(tidybayes)
+
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+analysis_data <- read_parquet("data/analysis_data/analysis_data.parquet")
+
+analysis_data <- analysis_data |>
+  mutate(
+    gender = factor(gender),
+    occupation = factor(occupation),
+    subregion = factor(subregion),
+    time_period = factor(time_period)
+  )
+  
+# To make data reproducible
+set.seed(200)
 
 ### Model data ####
-first_model <-
+relevance_model <-
   stan_glm(
-    formula = flying_time ~ length + width,
+    formula = percentile_rank ~ subregion + log(years_since_birth) * time_period + gender + occupation,
     data = analysis_data,
     family = gaussian(),
     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
     prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
+    seed = 853,
+    cores = 4
   )
 
 
 #### Save model ####
 saveRDS(
-  first_model,
-  file = "models/first_model.rds"
+  relevance_model,
+  file = "models/relevance_model.rds"
 )
 
 

### 2024-11-27 paper/paper.qmd
updates paper code and pdf

@@
 top5_subregions <- cleaned_data_filtered |>
-  group_by(time_period) 
+  group_by(time_period) |>
   slice_max(order_by = n, n = 5) |>
@@
 
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
+<!-- ```{r} -->
+<!-- #| eval: true -->
+<!-- #| echo: false -->
+<!-- #| message: false -->
+<!-- #| warning: false -->
+<!-- #| label: fig-ppcheckandposteriorvsprior -->
+<!-- #| layout-ncol: 2 -->
+<!-- #| fig-cap: "Examining how the model fits, and is affected by, the data" -->
+<!-- #| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"] -->
 
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
+<!-- pp_check(first_model) + -->
+<!--   theme_classic() + -->
+<!--   theme(legend.position = "bottom") -->
 
-posterior_vs_prior(first_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
-```
+<!-- posterior_vs_prior(first_model) + -->
+<!--   theme_minimal() + -->
+<!--   scale_color_brewer(palette = "Set1") + -->
+<!--   theme(legend.position = "bottom") + -->
+<!--   coord_flip() -->
+<!-- ``` -->
 
-## Diagnostics
+<!-- ## Diagnostics -->
 
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
+<!-- @fig-stanareyouokay-1 is a trace plot. It shows... This suggests... -->
 
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
+<!-- @fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests... -->
 
-```{r}
-#| echo: false
-#| eval: true
-#| message: false
-#| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
-
-plot(first_model, "trace")
-
-plot(first_model, "rhat")
-```
+<!-- # ```{r} -->
+<!-- # #| echo: false -->
+<!-- # #| eval: true -->
+<!-- # #| message: false -->
+<!-- # #| warning: false -->
+<!-- # #| label: fig-stanareyouokay -->
+<!-- # #| fig-cap: "Checking the convergence of the MCMC algorithm" -->
+<!-- # #| fig-subcap: ["Trace plot", "Rhat plot"] -->
+<!-- # #| layout-ncol: 2 -->
+<!-- # -->
+<!-- # plot(first_model, "trace") -->
+<!-- # -->
+<!-- # plot(first_model, "rhat") -->
+<!-- # ``` -->
+<!-- # -->
 

### 2024-12-01 paper/paper.qmd
removes unnecessary files, updates LLM usage, updates model, updates and adds in sections of paper

@@
 ---
-title: "Which Factors are Associated with Wikipedia Relevancy?"
-subtitle: "An Analysis of Notable People on Wikipedia"
+title: "Analyzing Trends on the Characteristics of Notable People on Wikipedia"
+subtitle: "[BLAH, BLAH,BLAH] characteristics are associated with increased prominence"
 author: 
@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "Wikipedia is an online encyclopedia that contains information on millions of diverse subjects, arguably serving as a repository for human knowledge.
+In this paper, I analyzed a dataset of notable people on Wikipedia from 3500 BCE to 2018 AD to identify whether certain characteristics (such as age and gender) were correlated with prominence.
+The analysis found that [WHAT DID YOU FIND???].
+The findings highlight...."
 format: pdf
@@
 bibliography: references.bib
+toc: true
 ---
@@
 library(knitr)
+library(rstanarm)
+library(broom)
+library(tidymodels)
 
+raw_data <- read.csv(here::here("data/raw_data/raw_data.csv"))
 cleaned_data <- read_parquet(here::here("data/analysis_data/analysis_data.parquet"))
+training_data <- read_parquet(here::here("data/analysis_data/training_data.parquet"))
+testing_data <- read_parquet(here::here("data/analysis_data/testing_data.parquet"))
+
+BIC_model <- readRDS(here::here(file = "models/relevance_model.rds"))
 
@@
 
-Understanding prominence of individuals on offers a way to quantify the societal impact of individuals through time.
-By using a dataset of notable people on Wikipedia from 3500 BCE to 2018 AD, this paper uses a bayesian linear model to identify certain factors associated with prominence.
-Some of the factors focused on include nationality, gender, occupation, and the number of years since the individuals birth.
-Analysing potential trends allows us to evaluate potential patterns and bias in one's relevance.
+Wikipedia is an online encyclopedia that contains information on millions of diverse subjects, arguably serving as a repository for human knowledge.
+Within this vast encyclopedia, there is also a collection of biographical information on "notable people" who have lived spanning millennia.
+Thus, one research study [@notablepeople] compiled a dataset of notable people on Wikipedia from 3500 BCE to 2018.
+
+Using this dataset, I constructed a linear model to identify whether certain characteristics were associated with increased prominence.
+Some of the factors focused on include trends in geographical subregion, gender, occupation, and the number of years since the individuals birth.
+By analysing these factors, this paper aims to uncover potential bias in online biographical representation and contribute to a deeper understanding of factors connected to online prominence.
 
@@
 
-The estimating (or what we are estimating) is the prominence of their Wikipedia biography based on percentile.
+The estimand (or what is being estimated) is the prominence of their Wikipedia biography based on percentile.
 "Prominence" of a biography is determined using multiple metrics, such as the average amount of views per year, the total word count, and the number of Wikipedia editions.
+This constructed percentile variable is also a transformation of the variable `ranking_visib_5criteria` present in the original dataset.
+Features of this variable are elaborated on in @sec-measurement.
 
@@
 
-Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....
+Understanding which factors contribute to prominence on Wikipedia is essential for many reasons.
+Wikipedia is used as a crucial tool for obtaining information for millions of people worldwide, having the ability to shape perceptions of prominent individuals.
+Unequal representation of prominent people can perpetuate existing biases about which characteristics are seen as "ideal" for prominence.
+Furthermore, these biases can discourage some individuals from pursuing fields where prominent people sharing their characteristics are under represented.
+Thus, analysing these dynamics can help with addressing broader societal biases and striving for a more comprehensive view of individual prominence.
+
+Telegraphing paragraph: The remainder of this paper is structured as follows.
+@sec-data mentions features of the dataset, @sec-model introduces and explains the constructed model, @sec-results summarizes the results of the paper, and @sec-discussion discusses the significance of these findings.
 
@@
 
-All data analysis was done through the statistical programming language R [@citeR] with the packages `tidyverse`[@tidyverse], `rstanarm` [@rstanarm], `modelsummary` [@modelsummary], `arrow`[@arrow], `readr`[@readr], `httr`[@httr], `R.utils`[@R.utils], `knitr`[@knitr] and `ggplot2` [@ggplot].
+All data analysis was done through the statistical programming language R [@citeR] with the packages `tidyverse`[@tidyverse], `rstanarm` [@rstanarm], `modelsummary` [@modelsummary], `arrow`[@arrow], `readr`[@readr], `httr`[@httr], `R.utils`[@R.utils], `knitr`[@knitr], `tidymodels` and `ggplot2` [@ggplot].
 
-## Measurement [@sec-measurement]
+## Measurement {#sec-measurement}
 
-Wikipedia is an online encyclopedia that provides information on numerous subjects, including the lives of those who are relatively well-known.Thus, the data comes from a research study [@notablepeople] that aims to build a cross-verified database of 'notable people' who have ever lived by using information from Wikipedia.
-Those with a Wikipedia article are considered "notable", as the overwhelming majority of people who have ever lived do not have one.
+Wikipedia is an online encyclopedia that provides information on numerous subjects, including the lives of those who are relatively well-known.
+Using Wikipedia data, one research study [@notablepeople] aimed to build a cross-verified database of 'notable people' who have ever lived.
+Individuals with a Wikipedia article are considered "notable", as the overwhelming majority of people who have ever lived do not have one.
+This data was obtained using the Wikidata universe (which provides data on Wikipedia), where they used the "instance of humans" category to select for a sample of notable individuals.
 Additionally, this dataset of notable people is very large (with hundreds of thousands of entries), reflecting the large amount of notable people that are written about on Wikipedia.
 
-This data was obtained using the Wikidata universe (which provides data on Wikipedia), where they used the "instance of humans" category to select for a sample of notable individuals.
-Many potential obstacles (including identifying non-humans vs humans or multiple biographies) were controlled for when this dataset was made.
+The data was also verified by the researchers through numerous ways.
+One way was the cross-verification of information that used 7 different versions of Wikipedia and Wikidata to make sure that the versions are consistent.
+Manual checks of validity were also used by hiring teams from a diverse set of countries (France, the UAE, and India) to compare the information on their database to that on Wikipedia/Wikidata.
 
-Based on the information provided in those Wikipedia articles, the study was also able to identify characteristics of these people. Some of these factors include nationality, occupation, and age.
+Based on the information provided in those Wikipedia articles, the study was also able to identify numerous characteristics of these people - reflected by the 49 variables in the dataset.
+A more in-depth list of all these variables can be found in the appendix (@sec-variables-of-the-dataset).
+Some of these factors of interest for this analysis include ones geographic origin, occupation, and age.
 
@@
 
-## Data Cleaning and Variables
+More on the measurement of the dataset can be found in @sec-exploration, which provides an in-depth exploration on the methodology of the dataset, as well as its limitations.
 
-This dataset was cleaned by first mutating some variables, selecting/renaming variables of interest, and filtering out rows with missing information, randomly selecting 10,000 entries from the dataset.
+## Data Cleaning and Variables {#sec-data-cleaning-and-variables}
+
+This dataset was cleaned by first mutating some variables, selecting/renaming variables of interest, and filtering out rows with missing information.
 The variables selected are mentioned later on in this section.
@@
 
-- `**percentile_rank**`: a transformation of the variable `ranking_visib_5criteria` (as mentioned in @sec-measurement).
+-   **percentile_rank**: a transformation of the variable `ranking_visib_5criteria` (as mentioned in @sec-measurement).
 This indicates the percentile associated with the notability ranking.
@@
 
-- `**subregion**`: the UN subregion corresponding to where they were from. This is simply a renaming of the variable `un_subregion`.
+-   **subregion**: the UN subregion corresponding to where they were from. This is simply a renaming of the variable `un_subregion`.
 
-- `**years_since_birth**`: the number number of years that have passed since their birth. If they are alive, this is simple their age.
+-   **years_since_birth**: the number number of years that have passed since their birth. If they are alive, this is simply their age.
 
-- `**time_period**`: The time period that they were born in.
+-   **time_period**: The time period that they were born in.
 
-- `**gender**`: The reported gender of the individual (either male or female).
+-   **gender**: The reported gender of the individual (either male or female).
 
-- `**occupation**`: The primary field/occupation that the individual is known for.
+-   **occupation**: The primary field/occupation that the individual is known for.
 
-## Analysis of Variables
+## Analysis of Variables {#sec-analysis-of-variables}
 
-### Subregion
+### Subregion {#sec-subregion}
 
-In @fig-subregion-counts, we can visualize the distribution of each geographic sub region.
+@tbl-subregion_counts contains information on the different subregions as well as the proportion of notable people for each subregion.
 
 ```{r}
-
-#| label: fig-subregion-counts
-#| fig-cap: Proportion of Notable People by Subregion
+#| label: tbl-subregion_counts
+#| fig-cap: Proportion of Notable People On Wikipedia by Geographical Subregion
 #| echo: false
@@
   group_by(subregion) |>
-  summarize(Count = n()/nrow(cleaned_data)) |>
-  arrange(desc(Count))
+  summarize(Proportion = n()/nrow(cleaned_data)) |>
+  arrange(desc(Proportion))
 
@@
 ```
-@fig-subregion-counts provides a detailed view of the prevalence of notable people by subregion.
+
 Interestingly, subregions that are a part of the Western world tend to be over-represented in terms of notable people.
@@
 However, a notable feature of `years_since_birth` (and thus `time_period`) is the distribution as shown in @fig-years_since_birth.
+
 ```{r}
@@
 
+@fig-years_since_birth also has consequences for the `time_period` variable.
+There is an extreme lack of representation for those born in earlier time periods (especially before 500 AD), likely because of much documentation of notable people being lost from time.
+
 ### Time Period and Subregion
@@
 In @fig-time-subregion, we can see this relationship quite clearly.
-Note that the proportions are out of the top 5 most popular subregions, rather than every subregion.
+Note that the proportions are out of the top 5 most popular subregions instead of every subregion.
 This was done to ensure readability.
@@
 #| label: fig-time-subregion
-#| fig-cap: Top 5 Subregions by Time Period
+#| fig-cap: Top 5 Subregions of Notable People by Time Period. The graph illustrates the large variability of prominent subregions through time.
 #| echo: false
@@
 ```
+
 From @fig-time-subregion, we can confirm the relationship between the time period and subregion - that the prevalency of notable individuals heavily changes depending on the time period in question.
@@
 The remaining variables, gender and occupation, may also show some sort of trend (since ones field of work is often quite gendered).
-This relationship is shown in @tbl-gender-occupation, which shows ones occupation (or more specifically, what they are known for).
+This relationship is shown in @tbl-gender_occupation, which shows ones occupation (or more specifically, what they are known for).
 
 ```{r}
-#| label: tbl-gender-occupation
-#| fig-cap: Occupations of Notable People by Gender
+#| label: tbl-gender_occupation
+#| fig-cap: Occupations of Notable People by Gender, Showing High Proportion of Males
 #| echo: false
@@
 ```
-@tbl-gender-occupation shows that those of nobility (often by being born in a high social rank) tend to have a higher proportion of females, where other occupations - such as the military - tend to have a higher proportion of males.
+
+@tbl-gender_occupation shows that those of nobility (often by being born in a high social rank) tend to have a higher proportion of females, where other occupations - such as the military - tend to have a higher proportion of males.
 
@@
 
+@tbl-gender reinforces the phenomenon of notable people on Wikipedia being overwhelmingly male. In fact, the proportion of males is roughly 85%.
+
+```{r}
+#| label: tbl-gender
+#| fig-cap: Proportion of Notable People by Gender
+#| echo: false
+
+gender_table <- cleaned_data |>
+  summarize(
+    Count = n(),
+    female_count = sum(gender=="Female"),
+    male_count = sum(gender=="Male"),
+    proportion_female = female_count/Count,
+    proportion_male = male_count/Count) |>
+  arrange(desc(proportion_female))
+
+gender_table |>
+  kable()
+
+```
+
+# ***Make sure to include graph on occupation***
+
 # Model
 
-The goal of our modelling strategy is twofold. Firstly,...
+## Overview
 
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+The ultimate goal the modelling strategy is to estimate the prominence of individuals on Wikipedia (by percentile).
+The model incorporates interaction terms as well as validation techniques to ensure model robustness and accuracy.
+
+Additional background details and diagnostics are included in the Appendix [@sec-model-details].
 
@@
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+The model is expressed by the equation:
 
 \begin{align}
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
+\text{prominence percentile} = &\ \beta_0 + \beta_1 \cdot \text{occupation} + \beta_2 \cdot \text{subregion} + \beta_3 \cdot \text{time period} \\
+&+ \beta_4 \cdot \log(\text{age}) + \beta_5 \cdot \text{gender} + \beta_6 \cdot (\text{time period} \times \log(\text{age})) \\
+&+ \beta_7 \cdot (\text{occupation} \cdot \text{gender}) + \epsilon
 \end{align}
 
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+with the variables representing the following:
 
-### Model justification
+-   $\beta_0$ : the intercept term when all other predictors are set to zero.
+-   $\beta_1$ : the effect of ones occupation (relative to one with an occupation of an Academic) on prominence percentile ranking.
+-   $\beta_2$ : the effect of ones geographical subregion (relative to the Caribbean) on prominence percentile ranking.
+-   $\beta_3$ : the effect of ones time-period (relative to those born before 500AD) on prominence percentile ranking
+-   $\beta_4$ : the logarithmic effect of age (`years_since_birth`).
+-   $\beta_5$ : The effect of ones gender (relative to female) on prominence percentile ranking
+-   $\beta_6$ : the interaction between the individuals time period (at birth) and age
+-   $\beta_7$ : the interaction between ones occupation and their gender
+-   $\epsilon$ : residual term, or the variation in percentile_ranking not due to the predictors.
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+The model was ran in R [@citeR] using the base `lm()` function.
 
-We can use maths by including latex between dollar signs, for instance $\theta$.
+Many of the modelling decisions are reflective of the findings from the @sec-analysis-of-variables section. These include:
 
-# Results
+-   the decision to apply `log()` to the age, as the distribution of this variable followed an exponential distribution (thus transforming this variable aids with identifying these effects)
+
+-   Additionally, the decision to add an interaction term between the individual's age and time period is informed by how time period is a categorical representation of ones age (thus affecting one another)
+
+-   The decision to apply an interaction between gender and occupation. It was shown that gender ratios depend heavily on the occupation, making them strongly associated with one another.
+
+## Model Assumptions
+
+Linear regression relies on assumptions that should be verified before drawing inferences on the results of the model.
+These assumptions include linearity, homoscedasticity (constant variance), and normally distributed error (residuals).
+@fig-assumptions provides graphs that checks these assumptions.
+
+```{r}
+#| label: fig-assumptions
+#| fig-cap: Compilation of Graphs Verifying Assumptions of Linear Regression
+#| fig-subcap: ['Residuals vs Fitted Plot: Shows Roughly Linearity and Constant Variance', 'QQ-plot of Standardised Residuals: Shows Roughly Normally Distributed Standardised Error (Residuals)', 'Scale-location plot which shows homoscedasticity (Approximately Constant Variance)']
+#| echo: false
+
+par(mfrow = c(2,2))
+plot(BIC_model, which = 1)
+plot(BIC_model, which = 2)
+plot(BIC_model, which = 3)
+
+```
+
+# ELABORATE MORE ON LINEAR REGRESSION GRAPHS (SENTENCE or two for each graph)
+
+## Model Validation
+
+#### Bayesian information Criterion
+
+The Bayesian information criterion (BIC) is a metric used for model selection among a finite set of models.
+It is based on the likelihood function and penalises datasets that may be too large.
+This validation technique helps minimize overfitting while retaining the goodness of fit.
+(<https://ieeexplore.ieee.org/document/1311138>)
+
+This statistical metric was used as an aid in determining which predictor variables to remove and which variables to include in the final model.
+More details on how this method was used is found in the appendix (@sec-bic).
+
+#### Root Mean Squared Error
+
+Analysis of the root mean squared error (RMSE) can provide a clue as to how accurate the model's estimations are.
+Root mean squared error measures the average difference between values predicted by the model and the actual values.
+Using the `modelsummary()` function (as shown in @tbl-modelresults), the model obtained an RMSE of 0.26, which corresponds to an average error of 26 percentile ranks.
+
+#### Out-of-sample testing
+
+Further validation of the model, including the validation of linear regression assumptions, is done through out-of-sample testing.
+Training data on different models was used to generate predictive abilities for the model.
+Then, based on their predictions of the testing data, comparisons of the RMSE of different models indicated that the chosen model tended to perform better (a more accurate predictive model would tend to have a lower RMSE).
+More details on the different models tested and their comparisons can be found in @sec-rmse-comparison.
+
+## Limitations
+
+A notable limitation of this model is that it is theoretically possible for the model to estimate a negative percentile or a percentile above 100.
+However, since these estimations would be physically impossible, this suggests potentially inaccurate results for more extreme percentile estimates.
+
+Another limitation is the relative lack of data for some underrepresented groups.
+@sec-subregion, for example, illustrates the discrepency for certain subregions in the dataset.
+A comparative lack of data for those certain subregions are likely associated with less predictive certainty from the model.
+In other words, the models predictions of prominence for people in different time periods/contexts is likely less accurate.
+
+A final limitation of this model is that predicting prominence using a dataset on Wikipedia relies heavily on the informational accuracy of the original dataset.
+Incorrect information on the characteristics results in an inaccurate model.
+
+# Results {#sec-results}
 
@@
 
-library(rstanarm)
+testing_data$predicted_rank <- predict(BIC_model, testing_data) # prediction of model
 
-first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
 ```
@@
 ```{r}
+#| label: tbl-modelresults
+#| fig-cap: Output of modelsummary() for linear model, highlighting 6 of the most significant predictor variables.
+"Significance" was determined by co-efficients that have a p-value less than 0.05 that also large effect on prominence
 #| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
-#| warning: false
 
-modelsummary::modelsummary(
-  list(
-    "First model" = first_model
-  ),
-  statistic = "mad",
-  fmt = 2
+BIC_model <-lm(data = cleaned_data, percentile_rank ~  occupation + subregion + time_period + log(years_since_birth) + gender + time_period:log(years_since_birth) + occupation:gender)
+
+model_tidy <- tidy(BIC_model)
+
+# Rank and filter the top 5 predictors by absolute value of coefficients
+top_predictors <- model_tidy %>%
+  mutate(abs_estimate = abs(estimate)) %>%
+  arrange(desc(abs_estimate)) %>%
+  filter(p.value < 0.025) |>
+  slice(1:8) |>
+  pull(term)
+
+# Display the top 5 predictors using modelsummary
+modelsummary(BIC_model,
+  coef_map = top_predictors)
+
+```
+
+the `modelsummary()`function from the `modelsummary` package (@modelsummary) provides a summary for the findings of the linear model, and is shown in @tbl-modelresults to highlight the top 6 most significant characteristics that affect Wikipedia prominence.
+Aside from the time period, the most significant coefficients of the model were occupation-related.
+
+```{r}
+#| label: fig-gender_prediction
+#| fig-cap: Boxplot of Model Predictions for Prominence by Gender
+#| echo: false
+
+gender_data <- testing_data |>
+  group_by(gender) |>
+  mutate(
+    mean_predicted_rank = mean(predicted_rank, na.rm = TRUE),
+    median_predicted_rank = median(predicted_rank, na.rm = TRUE),
+    count = n()
+  )
+
+ggplot(gender_data, aes(x = gender, y = predicted_rank, fill = gender)) +
+  geom_boxplot() +
+  theme_minimal() +
+  labs(
+    x = "Gender",
+    y = "Predicted Percentile Rank"
+  ) +
+  scale_fill_manual(values = c("Male" = "steelblue", "Female" = "coral")) +
+  theme(legend.position = "none")
+
+```
+
+```{r}
+#| label: fig-time_period_prediction
+#| fig-cap: Model-Predicted Distributions of Percentile Rank by Time Period. The graph illustrates a much higher prominence for those born before 500 AD
+#| echo: false
+
+testing_data$predicted_rank <- predict(BIC_model, testing_data)
+
+time_period_stats <- testing_data %>%
+  group_by(time_period) %>%
+  summarize(
+    mean = mean(predicted_rank, na.rm = TRUE),
+    sd = sd(predicted_rank, na.rm = TRUE)
+  )
+
+x_vals <- seq(
+  min(testing_data$predicted_rank, na.rm = TRUE),
+  max(testing_data$predicted_rank, na.rm = TRUE),
+  length.out = 5000
+)
+
+# Generate normal distributions
+normal_distributions <- time_period_stats |>
+  rowwise() |>
+  mutate(
+    x = list(x_vals),
+    density = list(dnorm(x_vals, mean = mean, sd = sd))
+  ) |>
+  unnest(cols = c(x, density))
+
+ggplot(normal_distributions, aes(x = x, y = density, color = time_period, fill = time_period)) +
+  geom_line(size = 1.2) +  # Density curve
+  geom_area(alpha = 0.2, position = "identity") +  # Filled area
+  geom_vline(aes(xintercept = mean), linetype = "solid", linewidth = 0.8) +  # Mean
+  geom_errorbarh(aes(xmin = mean - 1.96 * sd, xmax = mean + 1.96 * sd, y = 0), 
+                 height = 0.1, color = "black", linetype = "dashed") +  # Confidence intervals
+  facet_wrap(~time_period, ncol = 1, scales = "free_y") +  # Vertical facets by time period
+  theme_minimal() +
+  scale_y_continuous( breaks = seq(0, 4, by = 2)) +
+  labs(
+    x = "Predicted Percentile Rank",
+    y = "Density"
+  ) +
+  theme(
+    strip.text = element_text(size = 14),
+    panel.spacing = unit(0.5, "lines")
   )
@@
 
-# Discussion
+```{r}
+#| label: fig-subregion_prediction
+#| fig-cap: Boxplot of Model's Predicted Prominence of Individuals Based on Geographical Subregion
+#| echo: false
 
-## First discussion point {#sec-first-point}
+coef(BIC_model)
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+# Or extract only the subregion coefficients
+subregion_coef <- coef(BIC_model)[grep("subregion", names(coef(BIC_model)))]
+subregion_coef
 
-## Second discussion point
+predicted_values <- predict(BIC_model, newdata = testing_data, type = "response")
 
-Please don't use these as sub-heading labels - change them to be what your point actually is.
+# Add predictions to the original dataframe
+testing_data$predicted_percentile_rank <- predicted_values
 
-## Third discussion point
+# Plot predicted percentile rank by subregion
+ggplot(testing_data, aes(x = predicted_percentile_rank, y = subregion, fill = subregion)) +
+  geom_boxplot() +
+  theme_minimal() +
+  labs(
+    x = "Predicted Percentile Rank",
+    y = "Subregion"
+  ) +
+  theme(
+    axis.text.y = element_text(angle = 0),  # Keeps the subregion names horizontal
+    legend.position = "none"  # Removes the legend
+  )
 
-## Weaknesses and next steps
+```
 
-Weaknesses and next steps should also be included.
+```{r}
+#| label: fig-percentile_prediction
+#| fig-cap: Graph comparing the model's predicted percentile of prominence vs.
+the actual percentile.
+Testing data (i.e., data the model was not trained with) was used to more accurately evaluate prediction ability.
+1000 random datapoints were selected to highlight the overall results.
+#| echo: false
 
-\newpage
+set.seed(200)
+
+graph_data <- testing_data |>
+  sample_n(1000)
+
+ggplot(data=graph_data,
+       aes(x=predicted_rank, y=percentile_rank)) + 
+  geom_point() + geom_smooth(aes(x=predicted_rank, y=percentile_rank))+
+  xlab("Predicted Percentile Rank by Model") + ylab("Actual Percentile Rank")
+
+```
+
+@fig-percentile_prediction highlights the trend between predicted prominence of the model compared to the actual prominence.
+The shadow of the blue line indicates the 95% confidence interval of predictions from the linear model.
+This illustrates a weak, but existing, relationship between the prediction given by the model and the actual percentile rank.
+
+# Discussion {#sec-discussion}
+
+(MAKE THIS SECTION \~100 LINES)
+
+## Notable Relationship between Time Period and Prominence
+
+Interestingly, time period tends to have quite a strong effect on prominence that is more significant than other characteristics that were evaluated for (such as subregion or gender).
+Notable individuals that were born before 500AD displaying higher prominence makes intuitive sense, as time may have resulted in many records of otherwise notable people not being included on Wikipedia.
+It is possible that those who were significantly influential or notable thousands of years ago tended to have more information being written about them, making their biographical records last longer.
+
+There is also a notable increase in prominence for those born between 501-1500AD, which might also be explained by the same phenomenon as those born before 500 AD.
+Interestingly, time periods after 1500 AD do not display this same trend in prominence, with those born between 1901-2020 AD having a higher mean prominence than those in 1501 AD.
+
+Future studies could specifically focus on the relationship between individual prominence and time periods, including the reason for those in time periods after 1500 AD not showing notable mean differences in prominence.
+
+## Geographic Subregion and Prominence
+
+https://data.worldbank.org/indicator/IT.NET.USER.ZS
+
+Using data from the World Bank, it is evident that countries that tend to have a larger prominence of internet users tend to be wealthier countries (with many of them being part of the western world).
+This was shown previously in @sec-analysis-of-variables, which suggested a significant overrepresentation of those from Europe and Northern America.
+
+Interestingly, the trend of western individuals being more notable does *not* continue when looking at already notable people (as shown by the lower predicted prominence of those from Oceania deemed to be part of the Western world).
+Even though the model underestimates the spread of the data, it is evident that those from Eastern Asia are an outlier in terms of prominence.
+
+## Similar Prominence Between Notable Men and Women
+
+some studies, including the one by [@Banaji_Greenwald], highlighted that unconscious gender stereotyping was present and that individuals assigned a higher assignment of fame to males than females.
+Another meta-analysis of gender inequality in the workplace by [@workplace_sexism] highlights sexism where women tend to receive less promotions and less leadership roles, among other factors.
+Women receiving less leadership and more lower-status roles in the workplace could easily translate into biases in societal prominence.
+
+However, the findings of this study do not entirely confirm previous studies between the relationship of gender and fame (which is heavily associated with prominence).
+In fact, the results relating to gender (shown in [@fig-gender_prediction]) highlight that notable women tend to be slightly more prominent than notable men.
+However, it also suggests that there is a large amount of variation in prominence  between notable men and women, indicating that gender is likely not a significant characteristic in predicting prominence from those who are already notable.
+
+It also may be possible that the underrepresentation of women in this dataset means that the women who are already notable require a higher threshold of prominence to be on the dataset in the first place.Future studies can be conducted to explore the relationship between already notable people and how gender may (or may not) be associated with prominence.
+
+## Discussion of modelsummary() results
+
+The results from the `modelsummary()`, which summarize the model, are shown in [@tbl-modelresults].
+Unsurprisingly, those that do not have their occupations mentioned (`occupationMissing` in `modelsummary()`) tend to be much less prominent overall.
+It is quite intuitive that a lack of information on an individual correlates to lower overall prominence.
+
+Interestingly, some occupations such as being involved in politics; being an important person in a large business; and being associated with sports or games also tend to have a notable effect on percentiles of prominence.  The results suggest that occupation plays quite an important role in determining prominence, at least compared to the other predictor variables.
+Additionally, those born in the time period from 1501-1700 AD and those from Central America tend to have a lower prominence.
+Future analyses could be done to explore whether there is genuinely a strong effect of these certain characteristics on prominence, as this also may indicate a potential flaw in the model.
+
+## Weaknesses
+
+### Results only relevant for those already considered "notable"
+
+analyses only takes into account people who are ALREADY PROMINENT.
+\@sec-analysis-of-variables identifies characteristics of prominent people, and the appearance of bias in favour of certain characteristics (such as being a man or from Western Europe) is already reflected.
+However, since this study measures difference in prominence between those who are **already** notable, the linear model does not tend to highlight those biases as strongly.
+
+### Unequal Distribution of Characteristics
+
+Not only has the world population grown exponentially in the past few hundred years, but records of notable people can be lost due to time.
+This can make predictions of prominence heavily biased towards individuals who live (or have lived) in more recent time periods.
+It may be difficult to extend the finding of prominence onto individuals with less represented characteristics (including being born before 500AD).
+
+### Limited Prediction Ability
+
+From \@fig-percentile_prediction, we can see the predictive ability of the model leaves a lot to be desired.
+It suggests that given the specific predictors of the model (related to gender, subregion, age, and broad categorization of occupation), there is still a lot of variability of prominence that is not explained by these predictors.
+This is further evident by the RMSE and R\^2 values shown in \@tbl-modelresults.
+The R\^2 value of 0.138 suggests that these predictors only explain 14% of the variance in `percentile_rank`, which is quite low.
+This suggests that an individuals prominence on Wikipedia is largely explained by other factors not included in the model (including ones that are not measured in the original dataset).
+
+We can also see that the model tends to put most of its predictions near the 50th-percentile mark.
+A more ideal model would have a more spread out prediction of percentile. This results in the model underestimating the overall spread/variance of the data, making some differences appear more stark than others.
+This phenomenon is also evident in figures that portray prediction results for given characteristics (such as \@fig-subregion_prediction, \@fig-time_period_prediction, and \@fig-gender_prediction).
+This means that the model largely underestimates the overall spread/variance of the data, resulting in characteristic-related differences appearing more significant than they actually are.
+
+although the predictive ability of this model leaves room for improvement, the model is still quite useful for analysing overall trends of prominence for specific characteristics.
+
+\`\newpage
 
@@
 
-# Appendix {-}
+# Appendix {.unnumbered}
 
@@
 
-## Posterior predictive check
+## Bayesian Information Criterion (BIC) {#sec-bic}
+
+## RMSE Comparison {#sec-rmse-comparison}
 
@@
 
+`{# {r} # plot(relevance_model, "trace") #  # plot(relevance_model, "rhat")`
+
 <!-- ```{r} -->
+
 <!-- #| eval: true -->
+
 <!-- #| echo: false -->
+
 <!-- #| message: false -->
+
 <!-- #| warning: false -->
+
 <!-- #| label: fig-ppcheckandposteriorvsprior -->
+
 <!-- #| layout-ncol: 2 -->
+
 <!-- #| fig-cap: "Examining how the model fits, and is affected by, the data" -->
+
 <!-- #| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"] -->
@@
 <!-- pp_check(first_model) + -->
+
 <!--   theme_classic() + -->
+
 <!--   theme(legend.position = "bottom") -->
@@
 <!-- posterior_vs_prior(first_model) + -->
+
 <!--   theme_minimal() + -->
+
 <!--   scale_color_brewer(palette = "Set1") + -->
+
 <!--   theme(legend.position = "bottom") + -->
+
 <!--   coord_flip() -->
+
 <!-- ``` -->
@@
 <!-- # ```{r} -->
+
 <!-- # #| echo: false -->
+
 <!-- # #| eval: true -->
+
 <!-- # #| message: false -->
+
 <!-- # #| warning: false -->
+
 <!-- # #| label: fig-stanareyouokay -->
+
 <!-- # #| fig-cap: "Checking the convergence of the MCMC algorithm" -->
+
 <!-- # #| fig-subcap: ["Trace plot", "Rhat plot"] -->
+
 <!-- # #| layout-ncol: 2 -->
+
 <!-- # -->
+
 <!-- # plot(first_model, "trace") -->
+
 <!-- # -->
+
 <!-- # plot(first_model, "rhat") -->
+
 <!-- # ``` -->
+
 <!-- # -->
+
+# Exploration of Notable People Dataset and Methodology {#sec-exploration}
+
+## Introduction
+
+This section of this appendix contains a more thorough analysis and exploration onto the dataset that was used for this analysis.
+The dataset, *A cross-verified database of notable people, 3500BC-2018AD* (@notablepeople), contains a quite thorough verification and collection to ensure accurate data.
+This is especially important because of the nature of online encyclopedias and the sheer amount of individuals that were analysed.
+
+## Data Source and Collection {#sec-collection}
+
+The database integrates information from both Wikipedia and Wikidata.
+The extracted data from Wikipedia comes from seven popular language editions: English, French, German, Spanish, Portuguese, and Swedish.
+Many notable people documented (30%) thus come from the 6 non-English Wikipedia editions that were examined.
+Information on individuals is verified using different language editions, ensuring more reliable data.
+
+Data is also extracted from Wikidata, which contains structured data linked to a Wikipedia page.
+The sample of individuals chosen was defined by this data (The researchers then merged the information on both websites to avoid dealing with duplicates and ensure data reliability.
+
+### Data Verification
+
+Further verification was performed to ensure that the collected data was accurate.
+In addition to the reliability checks mentioned in @sec-collection, the researchers employed a series of algorithms, including ones that serve to:
+
+-   **decipher humans vs.
+non-humans** - a large number of entries were incorrectly identified as humans in Wikidata, which may include fictional characters or even music bands.
+The researchers used a list of expressions, including "list of", "duos", "bands," etc.
+that can identify faux-individuals.
+These entries were then removed from the dataset.
+
+-   **eliminate duplicate biographies** **(deduplication)** - some individuals have more than one Wikipedia biography.
+The algorithm used nearly a dozen different methods to ensure duplicates are not present.
+One example is aggressive standardization of names/titles, allowing easier identification of duplicates.
+
+### Variables of the dataset {#sec-variables-of-the-dataset}
+
+```{r}
+#| label: tbl-variables_of_raw_data
+#| tbl-cap: Table of all variables present in the dataset
+#| echo: false
+
+variable_names <- colnames(raw_data)
+
+variable_names_matrix <- matrix(variable_names, ncol = 2, byrow = TRUE)
+
+kable(variable_names_matrix)
+
+```
+
+The dataset includes a vast amount of variables (49) for each individual These variables display information relating to:
+
+-   Basic Demographic information: variables such as `name`, `birth`, `death`, `gender`, as well as geography-related variables such as `birthplace_name`, `deathplace_name`.
+Other variables, including `bplo1`, `dplo1`, `blpa1`, and `dpla1`, correspond to the longitude and latitude of these names (with `bp`, `dp` indicating birthplace/deathplace and `lo1`, `la1` indicating longitude/latitude).
+
+-   Domain of Influence: three sets of variables that are categorized hierarchically, corresponding to their predominant occupation or reason for prominence.
+`level1` variables correspond to one of 6 broad domains (e.g.
+culture, sports), `level2` variables correspond to fifteen subdomains (e.g., mathematician, politician), and `level3` variables corresponding to the specific occupation or domain of influence.
+
+-   Wikipedia-related Metrics: variables such as `number_wiki_editions` (number of different Wikipedia editions), `non_missing_score` (number of non-missing items from Wikipedia/Wikidata relating to demographic information), `total_count_words` (number of words in all biographies from Wikipedia), and `wiki_readers_2015_2018` (average yearly number of readers from 2015-2018)
+
+    There are also some variables that were constructed by the researchers, including variables which measure prominence.
+Alternate rankings of prominence instead of `ranking_visib_5_criteria` include `sum_visib_ln_5criteria`, which is the sum of the log of the 5 variables plus one (the 5 variables used for this ranking are mentioned in @sec-measurement).
+
+### Sampling of the Dataset
+
+The researchers defined the sample of notable individuals by using the "instance of individuals" category present on Wikidata.
+
+## Strengths of Dataset
+
+-   Robust data-verification: the researchers employed a variety of algorithms and methods to make sure that the data was accurate.
+These checks are also quite essential, as encyclopedias on hundreds of thousands of individuals is bound to have potential errors.
+
+-   Comprehensive: The inherent goal of the study results in numerous different regions, time periods, and domains of influence being included.
+Thus, this large scope allows the dataset to be quite broad and applicable to many different situations.
+
+-   Diverse sources: The researchers obtained information on prominent individuals using 7 different Wikipedia language editions, which reduces Anglosphere bias and improves representation.
+
+-   Numerous amount of variables: The large amount of variables (49) not only allows the opportunity for many different types of analysis, but also highlights the large amount of information obtained for most individuals in the dataset.
+
+## Limitations of Dataset
+
+## Potential Enhancements for Measuring Prominence
+
+###
+
+###
 

### 2024-12-01 scripts/03-clean_data.R

@@ -17,7 +17,7 @@ library(arrow)
 raw_data <- read_csv("data/raw_data/raw_data.csv")
 
 # To make data reproducible
-set.seed(200)
+set.seed(201)
 
 
 #Selecting for relevant columns, as well as making a couple new ones
@@ -26,9 +26,10 @@ cleaned_data <- raw_data |>
     percentile_rank = percent_rank(-ranking_visib_5criteria),
     years_since_birth = 2024-birth
     ) |>
-  select(name, years_since_birth, gender, level2_main_occ, bigperiod_birth_graph_b, un_subregion, percentile_rank) |> 
-  filter(if_all(c(years_since_birth, gender, level2_main_occ, bigperiod_birth_graph_b, un_subregion, percentile_rank), ~ !is.na(.))) |>
-  sample_n(10000, replace = FALSE) |>
+  select(years_since_birth, gender, level2_main_occ, bigperiod_birth_graph_b, un_subregion, percentile_rank) |> 
+  filter(gender %in% c("Male", "Female"),
+    if_all(c(years_since_birth, gender, level2_main_occ, bigperiod_birth_graph_b, un_subregion, percentile_rank), ~ !is.na(.))) |>
+  # sample_n(20000, replace = FALSE) |>
   rename(
     occupation = level2_main_occ,
     time_period = bigperiod_birth_graph_b,
@@ -47,6 +48,13 @@ cleaned_data <- raw_data |>
       )
   )
 
+
+# Filter and sample 1000 entries for each time period
+# sampled_data <- cleaned_data |>
+#   filter(time_period %in% c("1. Before 500AD", "2. 501-1500AD", "3. 1501-1750AD", "4. 1751-1900AD", "5. 1901-2020AD")) |> # Filter for the desired time periods
+#   group_by(time_period) |> # Group by time period
+#   sample_n(1000, replace = FALSE) |> # Sample 1000 from each group without replacement
+#   ungroup() # Remove the grouping
 
 
 #### Save data ####

### 2024-12-01 scripts/06-model_data.R

@@ -11,7 +11,9 @@
 #### Workspace setup ####
 library(tidyverse)
 library(rstanarm)
-library(tidybayes)
+library(MLmetrics)
+library(tidymodels)
+library(broom)
 
 
 #### Read data ####
@@ -28,23 +30,87 @@ analysis_data <- analysis_data |>
 # To make data reproducible
 set.seed(200)
 
+#formula = percentile_rank ~  subregion + log(years_since_birth) * time_period + gender + occupation,
+
+
+### Training and Test Split ###
+split <- initial_split(analysis_data, prop = 0.7)
+
+training_data <- training(split)
+testing_data <- testing(split)
+
 ### Model data ####
-relevance_model <-
-  stan_glm(
-    formula = percentile_rank ~ subregion + log(years_since_birth) * time_period + gender + occupation,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    seed = 853,
-    cores = 4
+relevance_model <- stan_glm(
+  percentile_rank ~  occupation + subregion + years_since_birth + 
+    gender + occupation:gender,  # Interaction as fixed effect
+  data = training_data,
+  family = gaussian(),
+  prior = normal(0, 1),
+  prior_intercept = normal(0.5, 1),
+  cores = 4
+)
+
+
+### Model informed by BIC ###
+
+relevance_model <- lm(data = training_data, percentile_rank ~  occupation + subregion + time_period + log(years_since_birth) + 
+                        gender + time_period:log(years_since_birth) + occupation:gender)
+
+stepfit = stats::step(relevance_model,
+               direction="backward", 
+               k = log(2))
+
+
+orig_model <-  lm(data = training_data, percentile_rank ~ occupation + log(years_since_birth))
+
+BIC_model <-lm(data = training_data, percentile_rank ~  occupation + subregion + time_period + log(years_since_birth) + 
+                 gender + time_period:log(years_since_birth) + occupation:gender)
+
+plot(BIC_model, which = 1)
+plot(BIC_model, which = 2)
+plot(BIC_model, which = 3)
+
+### Model Evaluation ###
+
+
+pog <- posterior_predict(relevance_model, newdata = testing_data)
+
[…]

### 2024-12-04 other/datasheet/datasheet_template.qmd
updates model section, adds simulations + data analysis, adds in datasheet, and updates paper

---
title: "Datasheet for 'A cross-verified database of notable people, 3500BC-2018AD'"
author: 
  - Parth Samant
thanks: "Code and data are available at: https://github.com/samantparth/Wikipedia-Historical-Prominence-Trends"
date: "December 2 2024"
format: pdf
number-sections: true
bibliography: references.bib
---

Extract of the questions from @gebru2021datasheets.

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created to address specific questions in social science, particularly relating to gender, economic growth, and urban/cultural development,
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The dataset was created by a research group from multiple different universities across the world.
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - This article was funded from grants by LIEPP (ANR-11-LABX-0091, ANR-11-IDEX-0005–02)  
4. *Any other comments?*
    - No

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- Instances that comprise the dataset represent notable individuals with variables representing their characteristics.
2. *How many instances are there in total (of each type, if appropriate)?*
	- Over 2 million instances of notable people on the dataset
3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- It is a sample from a larger group of 'notable people'. I do not believe it is representative of the entire sample of notable people, since there is a bias towards both modern figures and ones in certain countries.
4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	- Each instance consists of rankings related to Wikipedia prominence (such as the number of readers), geographic information (such as place of birth), occupational information, and other demographic information such as their name and year of birth.
5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- No
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- Yes, many individuals have missing information, particularly information about years of death (since many people are still living).
7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- Yes, these are made explicit. the ranking_5criteria and the sum_ln_5criteria variables are variables that are a calculation of prominence based on 5 metrics relating to fame/prominence.
8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- No
9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- Since there are millions of entries, there are likely at least some errors. This may be related to their occupation, name, year of death, etc.
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- It is self contained and does not rely on any other datasets.
11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- No
12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- No
13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- Yes, these subpopulations include age, gender, name, year of birth, year of death, and their time period. These are identified from the Wikidata website that provides basic information on notable individuals
14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- Yes, since the dataset contains the name of everyone on there.
15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- No, since the data obtained is publically available.
16. *Any other comments?*
	- No

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- The data was indirectly derived and it was validated/verified through multiple techniques. Some of these validations include removing duplications and identifying incorrect (including fictional) instances of humans.
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- Wikipedia and Wikidata have mechanisms for which the data can be downloaded from ther website. Most of the demographic information comes from a raw Wikidata dataset, where the researchers perform data cleaning to make it accurate.
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- No
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- Researchers were involved and they were compensated through the grants.
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- The timeframe is notable people born anywhere between 3500BC and 2018 AD.
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- No
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- Obtained it from a publically accessible website, the Sciences-Po Dataverse
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- No, they were not notified
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- No
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- N/A
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- No, an analysis has not been conducted on this specific dataset relating to its impact on data subjects.
12. *Any other comments?*
	- No

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- Yes, they eliminated multiple instances of the same person and removed instances of fictional people. They also created many of their own variables that are an amalgamation of existing variables, such as a ranking of each individual by prominence. 
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- No
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- Yes, the code that they used to preprocess the data was given. The link can be found on their github: https://medialab.github.io/bhht-datascape/
4. *Any other comments?*
	- No

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- Other than this repository, I was unable to find other instances that used this same dataset.
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- No
3. *What (other) tasks could the dataset be used for?*
	- It can be used for:
	  - evaluating bias of the amount of notable people by region
	  - analysing life expectancy based on the country of origin
	  - seeing which occupations notable people tend to have most often

4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- Yes, since certain characteristics may be biased (such as an overrepresentation of men, people from Europe, and people from the modern era), future uses may have a higher chance of analysing this dataset for bias. 
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- No
6. *Any other comments?*
	- No

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- Yes - the dataset is publically available from Sciences Po, which is a universtiry in Paris. 
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- The dataset is distributed through the Sciences Po dataverse. It has a DOI: https://doi.org/10.21410/7E4/RDAG3O.
3. *When will the dataset be distributed?*
	- There is no set date for releases, but it tends to be once every few years.
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- No, the article is open access and licensed under a Creative Commons Attribution 4.0 International License
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- No
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- No
7. *Any other comments?*
	- No

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- The dataset is hosted and maintainedby SciencesPo, with 6 authors that update the dataset every few years.
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- The authors can be contacted directly through email, which is contained on their GitHub website.
3. *Is there an erratum? If so, please provide a link or other access point.*
	- No
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- The dataset is updated every few years, and new updates are uploaded onto their github website
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- No, since the dataset obtains data from Wikipedia.
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- Yes, they are hosted and they are featured on their GitHub website
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- Yes, since the dataset is publically accessible to anyone, anyone can augment or extend the parametres of the dataset if they so wish. They can notify the authors by email if they believe it would be singificant for the goal of identifying notable people. The contributions do not have to be validated because of the nature of the dataset's distribution.
8. *Any other comments?*
	- No

\newpage

# References

### 2024-12-04 paper/paper.qmd
updates model section, adds simulations + data analysis, adds in datasheet, and updates paper

@@
 library(knitr)
-library(rstanarm)
 library(broom)
 library(tidymodels)
+library(MLmetrics)
 
-raw_data <- read.csv(here::here("data/raw_data/raw_data.csv"))
 cleaned_data <- read_parquet(here::here("data/analysis_data/analysis_data.parquet"))
@@
 
-Overview paragraph
+Wikipedia is an online encyclopedia has been one of the most popular references of information globally.
+Containing milllions of articles on the platform, and thus acting somewhat as an archive for human information.
+This encyclopedia provides information on a diverse range of topics from history to entertainment.
 
-Wikipedia is an online encyclopedia that contains information on millions of diverse subjects, arguably serving as a repository for human knowledge.
-Within this vast encyclopedia, there is also a collection of biographical information on "notable people" who have lived spanning millennia.
+Within this vast encyclopedia, there is also a collection of biographical information on "notable people" who have ever lived in the past few thousand years.
 Thus, one research study [@notablepeople] compiled a dataset of notable people on Wikipedia from 3500 BCE to 2018.
@@
 Using this dataset, I constructed a linear model to identify whether certain characteristics were associated with increased prominence.
-Some of the factors focused on include trends in geographical subregion, gender, occupation, and the number of years since the individuals birth.
-By analysing these factors, this paper aims to uncover potential bias in online biographical representation and contribute to a deeper understanding of factors connected to online prominence.
-
-Estimand paragraph
+Some of the factors focused on include geographical subregion, gender, occupation, and time period (at birth).
+By analysing these factors, this paper aims to uncover potential bias in characteristics of notable people and contribute to a deeper understanding of factors connected to prominence on Wikipedia.
 
@@
 
-Results paragraph
+The findings of this paper showed that an individuals time period and occupation/field have a large effect on an individuals prominence.
+Those who were born in earlier time periods (such as before 500 BCE) were associated large increases in prominence.
+Additionally, those known for being part of a noble class, an important family, or for creative endeavors that shape culture (such as musicians, actors, or painters) also tend to have higher overall prominence.
 
-Why it matters paragraph
+Subregion was somewhat associated with prominence, but with a large amount of variability.
+Notable individuals from Eastern Asia tend to have high levels of prominence, whereas those from Central America and Southern Africa have less.
+
+This paper also found that within those who are already prominent, gender tends to have a somewhat insignificant effect.
 
@@
 
-Telegraphing paragraph: The remainder of this paper is structured as follows.
-@sec-data mentions features of the dataset, @sec-model introduces and explains the constructed model, @sec-results summarizes the results of the paper, and @sec-discussion discusses the significance of these findings.
+The remainder of this paper is structured as follows.
+@sec-data mentions features of the dataset, @sec-model introduces, explains, and justifies the constructed model, @sec-results summarizes the results of the paper, and @sec-discussion discusses the significance of these findings.
 
@@
 
-All data analysis was done through the statistical programming language R [@citeR] with the packages `tidyverse`[@tidyverse], `rstanarm` [@rstanarm], `modelsummary` [@modelsummary], `arrow`[@arrow], `readr`[@readr], `httr`[@httr], `R.utils`[@R.utils], `knitr`[@knitr], `tidymodels` and `ggplot2` [@ggplot].
+All data analysis was done through the statistical programming language R [@citeR] with the help of the packages `tidyverse`[@tidyverse], `modelsummary` [@modelsummary], `arrow`[@arrow], `readr`[@readr], `httr`[@httr], `R.utils`[@R.utils], `knitr`[@knitr], `tidymodels` [@tidymodels], and `ggplot2` [@ggplot].
 
@@
 
-This dataset was cleaned by first mutating some variables, selecting/renaming variables of interest, and filtering out rows with missing information.
+This dataset was cleaned by first mutating some variables, selecting/renaming variables of interest, filtering out rows with missing information, and then randomly selecting 20,000 notable individuals.
 The variables selected are mentioned later on in this section.
 
-Since this paper focuses on predicting historical prominence, I chose variables which I thought could be associated with the outcome variable (`percentile_rank`).
+Since this paper focuses on predicting historical prominence, I initially chose variables which I thought could potentially be associated with the outcome variable (`percentile_rank`).
 
@@
 -   **percentile_rank**: a transformation of the variable `ranking_visib_5criteria` (as mentioned in @sec-measurement).
-This indicates the percentile associated with the notability ranking.
+This indicates the percentile associated with the prominence/notability ranking.
 A higher percentile indicates they were a more notable person.
 
-Predictor Variables:
+Original Predictor Variables:
 
@@
 
--   **years_since_birth**: the number number of years that have passed since their birth. If they are alive, this is simply their age.
+-   **years_since_birth**: the number of years that have passed since their birth. If they are alive, this is simply their age.
 
@@
 
--   **occupation**: The primary field/occupation that the individual is known for.
+-   **occupation**: The occupation (or possibly field/title) that the individual is known for.
+
+    -   Variables starting with "culture" refer to those who are known for producing immaterial goods
+
+        -   the 'culture-core' title refers to occupations that tend to be more artistic and creative in nature.
+These may include artists, writers, painters, or musicians (among others).
+Their contributions are often essential at shaping cultural values and aesthetics.
+
+        -   The 'culture-periphery' title refers to occupations that are still artistic/creative, but tend to include more commercial and applied work.
+These may include journalists, models, architects, or designers.
+
+    -   Other titles such as "family" and "nobility" highlight that they are predominanly known for being associated with an influential family or possessing a hereditary title in an aristocracy.
+
+    -   titles such as "Worker/Business (small)" refer to miscellaneous jobs that are not covered by other variables. These may include those who are well-known farmers, librarians, booksellers, etc.
+
+        -   This is different than "Other", which mostly includes those known for negative notorious acts (such as a criminal or serial killer).
+
+    -   a "Missing" occupation indicates that it was unable to be retrieved by the researchers.
 
@@
 #| label: tbl-subregion_counts
-#| fig-cap: Proportion of Notable People On Wikipedia by Geographical Subregion
+#| tbl-cap: Proportion of Notable People On Wikipedia by Geographical Subregion
 #| echo: false
@@
 
-Interestingly, subregions that are a part of the Western world tend to be over-represented in terms of notable people.
-In fact, the difference is so stark that the most well-represented region (Western Europe) has nearly 100x the representation of notable people than West Africa.
+Interestingly, subregions that are a part of the Western World tend to be over-represented in terms of notable people.
+In fact, the difference is so stark that the most well-represented region (Western Europe) has nearly 100 times the number of notable people than West Africa.
 
-There could be many explanations for this, such as how Western nations tend to have more global cultural dominance (and thus more 'notable people').
+There could be many explanations for the over representation of Western countrise, such as how Western nations tend to have more global cultural dominance (and thus more 'notable people').
 
-### time_period/years_since_birth
+### time_period/years_since_birth variables
 
 These are two variables that are directly associated with each other, since the time period of ones life is directly a result of the number of years since their birth.
+These were both originally included to highlight the influence of not only the time period, but the more specific year in which an individual as born.
 
-However, a notable feature of `years_since_birth` (and thus `time_period`) is the distribution as shown in @fig-years_since_birth.
+A notable feature of `years_since_birth` (and thus `time_period`) is the distribution as shown in @fig-years_since_birth.
 
@@
 This makes sense, as retrieving information on individuals that lived a longer time ago is more difficult.
-Future plots and analyses will thus use the logarithm of this variable to have a more detailed view on its impact.
 
@@
 Note that the proportions are out of the top 5 most popular subregions instead of every subregion.
-This was done to ensure readability.
+This was done to ensure readability and show overall trends.
 
@@
 
-### Gender and Occupation
+### Gender, Occupation, and their Interaction
 
 The remaining variables, gender and occupation, may also show some sort of trend (since ones field of work is often quite gendered).
-This relationship is shown in @tbl-gender_occupation, which shows ones occupation (or more specifically, what they are known for).
+This relationship is shown in [@tbl-gender-occupation], which shows ones occupation (or more specifically, what they are known for).
 
 ```{r}
-#| label: tbl-gender_occupation
-#| fig-cap: Occupations of Notable People by Gender, Showing High Proportion of Males
+#| label: tbl-gender-occupation
+#| tbl-cap: Occupations of Notable People by Gender, Showing High Proportion of Males
 #| echo: false
@@
 
-@tbl-gender_occupation shows that those of nobility (often by being born in a high social rank) tend to have a higher proportion of females, where other occupations - such as the military - tend to have a higher proportion of males.
+@tbl-gender-occupation shows that those of nobility (often by being born in a high social rank) tend to have a higher proportion of females, where other occupations - such as the military - tend to have a higher proportion of males.
 
-Interestingly, even the most female-dominated occupation (nobility) is still roughly 2/3rds men.
+Interestingly, even the most female-dominated 'occupation' (the family title, which means they are notable for being a part of an important family) is still roughly 2/3rds men.
 This reflects a clear bias in people that are considered 'notable': men are very much over-represented in every occupation (and in this dataset, as a result).
 
-@tbl-gender reinforces the phenomenon of notable people on Wikipedia being overwhelmingly male. In fact, the proportion of males is roughly 85%.
+[@tbl-gender] reinforces the phenomenon of notable people on Wikipedia being overwhelmingly male. In fact, the proportion of males is roughly 85%.
 
@@
 #| label: tbl-gender
-#| fig-cap: Proportion of Notable People by Gender
+#| tbl-cap: Proportion of Notable People by Gender, Showing Male Over Representation
 #| echo: false
@@
 
-# ***Make sure to include graph on occupation***
+Furthermore, @fig-occupation_count provides a visualization of the most common occupations in the dataset.
 
-# Model
+```{r}
+#| label: fig-occupation_count
+#| fig-cap: Number of Notable People by Occupation, Highlighting an Unequal Distribution
+#| echo: false
+
+occupation_summary <- cleaned_data %>%
+  count(occupation, name = "count")
+
+ggplot(occupation_summary, aes(x = count, y = reorder(occupation, count))) +
+  geom_bar(stat = "identity", fill = "skyblue", color = "black") + 
+  labs(x = "Count",
+    y = "Occupation"
+  ) 
+```
+
+Evidently, some occupations tend to be very over-represented, such as Sports/Games, Culture-core (refer to [@sec-analysis-of-variables]), or Politics.
+This highlights that notable people on Wikipedia are most often associated with only a handful of occupations/categories.
+
+# Model {#sec-model}
 
@@
 
-The ultimate goal the modelling strategy is to estimate the prominence of individuals on Wikipedia (by percentile).
-The model incorporates interaction terms as well as validation techniques to ensure model robustness and accuracy.
+The ultimate goal the modelling strategy is to identify which characteristics are most associated with prominence.
+The model was split up into testing and training sets with the help of the `tidymodels` [@tidymodels] package.
 
@@
 \text{prominence percentile} = &\ \beta_0 + \beta_1 \cdot \text{occupation} + \beta_2 \cdot \text{subregion} + \beta_3 \cdot \text{time period} \\
-&+ \beta_4 \cdot \log(\text{age}) + \beta_5 \cdot \text{gender} + \beta_6 \cdot (\text{time period} \times \log(\text{age})) \\
-&+ \beta_7 \cdot (\text{occupation} \cdot \text{gender}) + \epsilon
+&+ \beta_4 \cdot \text{gender} + \epsilon
 \end{align}
@@
 -   $\beta_3$ : the effect of ones time-period (relative to those born before 500AD) on prominence percentile ranking
--   $\beta_4$ : the logarithmic effect of age (`years_since_birth`).
--   $\beta_5$ : The effect of ones gender (relative to female) on prominence percentile ranking
--   $\beta_6$ : the interaction between the individuals time period (at birth) and age
--   $\beta_7$ : the interaction between ones occupation and their gender
+-   $\beta_4$ : The effect of ones gender on prominence percentile ranking
 -   $\epsilon$ : residual term, or the variation in percentile_ranking not due to the predictors.
 
-The model was ran in R [@citeR] using the base `lm()` function.
+The model was ran in the R programming language [@citeR] using the base `lm()` function, with the help of the `MLmetrics` and `broom` packages for model evaluation (shown in @sec-model-details of the appendix).
 
-Many of the modelling decisions are reflective of the findings from the @sec-analysis-of-variables section. These include:
+Many of the initial modelling decisions are reflective of the findings from the data section (in @sec-analysis-of-variables).
+However, these were later removed after performing various statistical tests.
+The initial decisions included:
 
--   the decision to apply `log()` to the age, as the distribution of this variable followed an exponential distribution (thus transforming this variable aids with identifying these effects)
+-   Applying `log()` to the age, as the distribution of this variable followed an exponential distribution (thus transforming this variable aids with identifying these effects).
 
--   Additionally, the decision to add an interaction term between the individual's age and time period is informed by how time period is a categorical representation of ones age (thus affecting one another)
+-   Adding an interaction term between the individual's age and time period, as time period is a categorical representation of ones age (thus affecting one another).
 
--   The decision to apply an interaction between gender and occupation. It was shown that gender ratios depend heavily on the occupation, making them strongly associated with one another.
+-   Adding an interaction between gender and occupation. It was shown that gender ratios depend heavily on the occupation, making them strongly associated with one another.
 
-## Model Assumptions
+The equation of the full model, which includes these initial decisions, is shown in @sec-model-details.
+
+## Checking Model Assumptions and Validation of Final Model
 
 Linear regression relies on assumptions that should be verified before drawing inferences on the results of the model.
-These assumptions include linearity, homoscedasticity (constant variance), and normally distributed error (residuals).
-@fig-assumptions provides graphs that checks these assumptions.
+These assumptions include a linear relationship between the dependent variable and independent variables, homoscedasticity (constant variance of the residual), normally distributed standard error (residuals), and no multicollinearity.
+@fig-assumptions provides graphs that checks the first three assumptions, with checks for multicollinearity being done in @sec-vif.
 
@@
 #| fig-cap: Compilation of Graphs Verifying Assumptions of Linear Regression
-#| fig-subcap: ['Residuals vs Fitted Plot: Shows Roughly Linearity and Constant Variance', 'QQ-plot of Standardised Residuals: Shows Roughly Normally Distributed Standardised Error (Residuals)', 'Scale-location plot which shows homoscedasticity (Approximately Constant Variance)']
+#| fig-subcap: ['Residuals vs Fitted Plot: Shows Approximate Linearity and Constant Variance', 'QQ-plot of Standardised Residuals: Shows Roughly Normally Distributed Standardised Error (Residuals)', 'Scale-location plot which shows homoscedasticity (Approximately Constant Variance)']
 #| echo: false
+#| layout-ncol: 2
 
-par(mfrow = c(2,2))
 plot(BIC_model, which = 1)
@@
 
-# ELABORATE MORE ON LINEAR REGRESSION GRAPHS (SENTENCE or two for each graph)
+@fig-assumptions provides a series of graphs that can help assess the few assumptions mentioned above. These plots show:
 
-## Model Validation
+-   linearity: the residuals vs fitted plot shows roughly uncorrelated residuals (evidenced by the red line) However, there is a slight decrease in fitted values closer to 0 and a slight increase in fitted values close to 1.
+This is possibly a consequence of how percentiles are not entirely normally distributed.
+Although the residuals appear to decrease as the fitted values increase, the trend line shows that the average value of the residual remains relatively constant.
+
+-   Homoscedasticity (constant variance): the scale-location plot evalutes the homoscedasticity of the model.
+The red line (corresponding to the averages of the fitted values based on standardised residuals) is roughly horizontal.
+
+-   Normally distributed standardised residuals: The QQ-plot shows that the standardised residuals are roughly normally-distributed, with a somewhat heavy tail for more extreme values.
+
+Furthermore, checks for multicollinearity were done to ensure that proper significance was identified for coefficients.
+As mentioned before, the specific checks are found in @sec-vif.
+This motivated the removal of the `years_since_birth` term - contributing to less multicollinearity and more accurate conclusions about coefficient significance, especially related to time period.
+
+### Validation of Final Model
+
+A series of statistical tools and techniques were used to aid in the ultimate goal of this model, which was to identify which characteristics correlate the most to individual prominence on Wikipedia.
+These tools were used in conjunction with tests of linear regression assumptions and analysis of the Variance Inflation Factor (VIF).
 
@@
 It is based on the likelihood function and penalises datasets that may be too large.
-This validation technique helps minimize overfitting while retaining the goodness of fit.
-(<https://ieeexplore.ieee.org/document/1311138>)
+This validation technique helps minimize over fitting while retaining the goodness of fit (@BIC).
 
 This statistical metric was used as an aid in determining which predictor variables to remove and which variables to include in the final model.
+The results of the BIC on the full model encouraged removal of the interaction variable between gender and occupation.
 More details on how this method was used is found in the appendix (@sec-bic).
@@
 Root mean squared error measures the average difference between values predicted by the model and the actual values.
-Using the `modelsummary()` function (as shown in @tbl-modelresults), the model obtained an RMSE of 0.26, which corresponds to an average error of 26 percentile ranks.
+Using the `modelsummary()` function (as shown in @tbl-modelresults), the model obtained an RMSE of 0.27, which corresponds to an average error of 27 percentile ranks.
 
@@
 
-Further validation of the model, including the validation of linear regression assumptions, is done through out-of-sample testing.
-Training data on different models was used to generate predictive abilities for the model.
-Then, based on their predictions of the testing data, comparisons of the RMSE of different models indicated that the chosen model tended to perform better (a more accurate predictive model would tend to have a lower RMSE).
+Further validation of the model was done through out-of-sample testing.
+Training data on different models was used to generate the predictive abilities of different models.
+Then, based on their predictions of the testing data, comparisons of the RMSE of different models indicated that the chosen model, with less complexity, tended to perform roughly as well as the full model.
 More details on the different models tested and their comparisons can be found in @sec-rmse-comparison.
 
-## Limitations
+## Limitations {#sec-model-limitations}
 
@@
 In other words, the models predictions of prominence for people in different time periods/contexts is likely less accurate.
+This is also prevalent in other characteristics, such as occupation.
+This limitation of the model also has consequences for the results in @sec-results.
 
@@
 
-Our results are summarized in @tbl-modelresults.
+## modelsummary() results
+
+The `modelsummary()`function from the `modelsummary` package (@modelsummary) provides a summary for the findings of the linear model, and is shown in @tbl-modelresults to highlight the most significant characteristics that affect Wikipedia prominence.
+Aside from the time period, the most significant coefficients of the model were occupation-related.
 
@@
 
+# initializes model prediction for the results
+
 testing_data$predicted_rank <- predict(BIC_model, testing_data) # prediction of model
@@
 #| label: tbl-modelresults
-#| fig-cap: Output of modelsummary() for linear model, highlighting 6 of the most significant predictor variables.
-"Significance" was determined by co-efficients that have a p-value less than 0.05 that also large effect on prominence
+#| fig-cap: Output of modelsummary() for linear model, highlighting  the most significant predictor variables as well as the effect of gender.
+"Significance" was determined by co-efficients that have a p-value less than 0.025 and a large effect on prominence.
 #| echo: false
-
-BIC_model <-lm(data = cleaned_data, percentile_rank ~  occupation + subregion + time_period + log(years_since_birth) + gender + time_period:log(years_since_birth) + occupation:gender)
 
@@
 
+top_predictors <- c(top_predictors, "genderMale")
+
 # Display the top 5 predictors using modelsummary
 modelsummary(BIC_model,
-  coef_map = top_predictors)
+  coef_map = top_predictors,
+   statistic = "p = {p.value}"
+)
 
@@
 
-the `modelsummary()`function from the `modelsummary` package (@modelsummary) provides a summary for the findings of the linear model, and is shown in @tbl-modelresults to highlight the top 6 most significant characteristics that affect Wikipedia prominence.
-Aside from the time period, the most significant coefficients of the model were occupation-related.
+Evidently, terms that are related to occupation and time period tend to the most correlated with Wikipedia prominence.
+Those involved in politics, big business, as well as those without a listed occupation are associated with the largest difference in prominence.
+Additionally, time periods that are more modern tend to also experience a larger decrease in prominence (compared to individuals born before 500 BCE), which is explored with more detail in @sec-prominence-and-time-period.
+
+## Prominence and Gender {#sec-prominence-}
+
+Those who are male also experienced a small (and not statistically significant) boost in notability among those who are already notable.
+Thus, to explore this trend of slightly higher male prominence, @fig-gender_prediction provides a view of the model's predictions for prominence divided by gender.
 
@@
 #| label: fig-gender_prediction
-#| fig-cap: Boxplot of Model Predictions for Prominence by Gender
+#| fig-cap: Densities of Gender-based Prominence Predictions
 #| echo: false
+#| warning: false
 
@@
 
-ggplot(gender_data, aes(x = gender, y = predicted_rank, fill = gender)) +
-  geom_boxplot() +
+gender_summary <- gender_data %>%
+  group_by(gender) %>%
+  summarise(
+    mean_rank = mean(predicted_rank, na.rm = TRUE),
+    sd_rank = sd(predicted_rank, na.rm = TRUE)
+  )
+
+# Create the density plot
+density_plot <- ggplot(gender_data, aes(x = predicted_rank, fill = gender)) +
+  geom_density(alpha = 0.5) +
   theme_minimal() +
   labs(
-    x = "Gender",
-    y = "Predicted Percentile Rank"
+    x = "Predicted Percentile Rank",
+    y = "Density"
   ) +
@@
 
+par(mfrow = c(1, 2))
+
+print(density_plot)
+
 ```
+
+The distribution of predicted prominence by gender is roughly equal, with women being very slightly higher.
+Despite men experiencing slightly higher prominence (as shown in @tbl-modelresults), the mean prediction of prominence favours women as shown in @tbl-gender_prediction.
+
+```{r}
+#| label: tbl-gender_prediction
+#| tbl-cap: Summary Statistics of Gender Prediction
+#| echo: false
+#| warning: false
+
+gender_summary <- gender_data %>%
+  group_by(gender) %>%
+  summarise(
+    mean_rank = mean(predicted_rank, na.rm = TRUE),
+    sd_rank = sd(predicted_rank, na.rm = TRUE)
+  )
+
+# Print the summary table
+# Use the base R method for printing
+gender_summary |>
+  kable(col.names=c("gender", "Mean Predicted Percentile", "standard deviation"))
+```
+
+## Prominence and Time Period {#sec-prominence-and-time-period}
+
+From the results of the `modelsummary()` function in @tbl-modelresults, it is evident that time period tends to have a large effect on prominence.
+Thus, @fig-time_period_prediction shows the effect of time period on model estimates with time periods categorised into five broad ranges.
 
@@
 #| label: fig-time_period_prediction
-#| fig-cap: Model-Predicted Distributions of Percentile Rank by Time Period. The graph illustrates a much higher prominence for those born before 500 AD
+#| fig-cap: Model-Predicted Distributions of Percentile Rank by Time Period.
+Bars Shown On the Bottom Denote the Standard Deviation of the Prediction, With More Variability for Less Represented Time Periods (such as before 500 AD)
 #| echo: false
-
-testing_data$predicted_rank <- predict(BIC_model, testing_data)
+#| warning: false
 
@@
   labs(
-    x = "Predicted Percentile Rank",
+    x = "Predicted Prominence Percentile",
     y = "Density"
@@
 
+@fig-time_period_prediction highlights the large variation in model predictions based on the time period the individual was born in.
+Although those born in earlier time periods tend to have significantly higher prominence, there were also a much lower amount of them.
+
+## Prominence and Subregion
+
+The relationship between subregion and predicted prominence is explored in @fig-subregion_prediction.
+
 ```{r}
 #| label: fig-subregion_prediction
-#| fig-cap: Boxplot of Model's Predicted Prominence of Individuals Based on Geographical Subregion
+#| fig-cap: Barplot of Model's Coefficients Associated With Subregion With 95% Confidence Interval. Values Are In Comparison To Dummy Variable for Subregion (Carribbean)
 #| echo: false
 
-coef(BIC_model)
+# Get all model coefficients
+model_coefficients <- coef(BIC_model)
 
-# Or extract only the subregion coefficients
-subregion_coef <- coef(BIC_model)[grep("subregion", names(coef(BIC_model)))]
-subregion_coef
+# Get the 95% confidence intervals for all coefficients
+conf_intervals <- confint(BIC_model, level = 0.95)
 
-predicted_values <- predict(BIC_model, newdata = testing_data, type = "response")
+# Combine the coefficients and confidence intervals into a data frame
+coef_df <- data.frame(
+  variable = names(model_coefficients),
+  coef_value = model_coefficients,
+  lower_ci = conf_intervals[, 1],
+  upper_ci = conf_intervals[, 2]
+)
 
-# Add predictions to the original dataframe
-testing_data$predicted_percentile_rank <- predicted_values
+# Filter for only the subregion-related variables (assuming the subregion names are part of the variable names)
+subregion_coef <- coef_df[grepl("subregion", coef_df$variable), ] 
+subregion_coef$variable <- gsub("^subregion", "", subregion_coef$variable)
 
-# Plot predicted percentile rank by subregion
-ggplot(testing_data, aes(x = predicted_percentile_rank, y = subregion, fill = subregion)) +
-  geom_boxplot() +
+subregion_coef_sorted <- subregion_coef %>%
+  arrange(desc(coef_value))
+
+ggplot(subregion_coef_sorted, aes(x = coef_value, y = reorder(variable, coef_value))) + 
+  geom_point(stat = "identity", fill = "lightblue", color = "black", size = 2.5) +  # Bars for coefficient values
+  geom_errorbarh(aes(xmin = lower_ci, xmax = upper_ci), height = 0.2, color = "black") +  # Error bars
+  labs(
+    x = "Coefficient Value",
+    y = "Subregion"
+  ) +
+  theme_minimal() + 
+   geom_vline(xintercept = 0, linetype = "dashed", color = "red", size = 0.5) + 
+  scale_x_continuous(limits = c(-0.4,0.4), 
+                     expand = c(0, 0))
+```
+
+@fig-subregion_prediction indicates how much certain subregions are correlated with increased prominence percentiles, as well as 95% confidence interval bars that show the uncertainty associated with each coefficients effect.
+Notable people from Central America are associated with over a 10 percent reduction in percentile prominence (compared to the Caribbean, which is the reference).
+This is in stark contrast to those from Eastern Asia, with that subregion being associated with the largest increase in prominence.
+
+## Prominence and Occupation
+
+@fig-occupation_results compares the different effects that occupations (or domains of influence) may have on the prominence of an individual.
+
+```{r}
+#| label: fig-occupation_results
+#| fig-cap: Comparison of Predicted (<span style="color:red;">Red</span>) vs Actual (<span style="color:blue;">Blue</span>) Prominence Percentile Rank by Occupation.
+It illustrates the predictive ability of the model while also showing the effect of occupation on prominence.
+#| echo: false
+
+ summary_data <- testing_data %>%
+  group_by(occupation) %>%
+  summarize(
+    mean_actual_rank = mean(percentile_rank, na.rm = TRUE),  # Actual ranks
+    mean_predicted_rank = mean(predicted_rank, na.rm = TRUE),  # Predicted ranks
+    .groups = "drop"
+  ) |>
+    arrange((mean_actual_rank)) |>
+   mutate(occupation = factor(occupation, levels = occupation))
+
+ggplot(summary_data, aes(y = reorder(occupation, mean_actual_rank))) +
+  geom_segment(
+    aes(x = mean_actual_rank, xend = mean_predicted_rank, y = occupation, yend = occupation)      
+  ) +
+  geom_point(
+    aes(x = mean_actual_rank), color = "blue", size = 3 
+  ) +
+  geom_point(
+    aes(x = mean_predicted_rank), color = "red", size = 3  
+  ) +
   theme_minimal() +
   labs(
-    x = "Predicted Percentile Rank",
-    y = "Subregion"
-  ) +
-  theme(
-    axis.text.y = element_text(angle = 0),  # Keeps the subregion names horizontal
-    legend.position = "none"  # Removes the legend
-  )
+    x = "Average Prominence Percentile Rank",
+    y = "Occupation")
 
 ```
+
+@fig-occupation_results highlights a large variation related to prominence and occupation.
+Those with an occupation/domain of influence that was unknown/missing tended to have the lowest prominence (by far), whereas those identified as being part of "culture-core" experienced the highest.
+The large difference between occupations also highlights the importance of occupation on prominence.
+
+## Overall Model Predictive Ability
+
+Furthermore, @fig-percentile_prediction provides a visualization of the predictive ability of the model that was used.
+Note that the ultimate purpose of the model not to predict prominence accurately, but rather to highlight which characteristics were most associated with prominence among notable people.
 
@@
 Testing data (i.e., data the model was not trained with) was used to more accurately evaluate prediction ability.
-1000 random datapoints were selected to highlight the overall results.
+500 random datapoints were selected to highlight the overall results.
 #| echo: false
@@
 graph_data <- testing_data |>
-  sample_n(1000)
+  sample_n(500)
 
@@
        aes(x=predicted_rank, y=percentile_rank)) + 
-  geom_point() + geom_smooth(aes(x=predicted_rank, y=percentile_rank))+
+  geom_point() + geom_smooth(aes(x=predicted_rank, y=percentile_rank), method = 'gam', formula = y ~ s(x, bs = "cs")) +
   xlab("Predicted Percentile Rank by Model") + ylab("Actual Percentile Rank")
@@
 @fig-percentile_prediction highlights the trend between predicted prominence of the model compared to the actual prominence.
-The shadow of the blue line indicates the 95% confidence interval of predictions from the linear model.
+The shadow of the blue line indicates the 95% confidence interval of the mean predictions from the linear model.
 This illustrates a weak, but existing, relationship between the prediction given by the model and the actual percentile rank.
@@
 
-(MAKE THIS SECTION \~100 LINES)
+## Notable Relationship between Time Period and Prominence {#sec-time-period-prominence}
 
-## Notable Relationship between Time Period and Prominence
-
-Interestingly, time period tends to have quite a strong effect on prominence that is more significant than other characteristics that were evaluated for (such as subregion or gender).
+Interestingly, time period tends to have quite a strong effect on prominence that is more significant than some other characteristics that were evaluated for (such as subregion or gender).
 Notable individuals that were born before 500AD displaying higher prominence makes intuitive sense, as time may have resulted in many records of otherwise notable people not being included on Wikipedia.
 It is possible that those who were significantly influential or notable thousands of years ago tended to have more information being written about them, making their biographical records last longer.
+This is captured in @fig-time_period_prediction, which highlights an exponentially lower amount of people that are from earlier time periods.
 
@@
 
-Future studies could specifically focus on the relationship between individual prominence and time periods, including the reason for those in time periods after 1500 AD not showing notable mean differences in prominence.
+Next steps for future studies could include exploring the amount of documentation of notable people through time and the distribution, exploring the relationship between the passage of time and the loss of documentation of individuals.
+It may be possible that time periods after the 1500's still retain most documentation of notable people, resulting in less differences in prominence and a larger sample.
 
@@
 
-https://data.worldbank.org/indicator/IT.NET.USER.ZS
+Using data from the World Bank (@worldbank), it is evident that countries that tend to have a larger prominence of internet users tend to be wealthier countries (with many of them being part of the western world).
+This finding was supported by the results in @sec-analysis-of-variables, which suggested a significant overrepresentation of those from Europe and Northern America.
 
-Using data from the World Bank, it is evident that countries that tend to have a larger prominence of internet users tend to be wealthier countries (with many of them being part of the western world).
-This was shown previously in @sec-analysis-of-variables, which suggested a significant overrepresentation of those from Europe and Northern America.
+@fig-subregion_prediction provides an overview on various coefficients for subregion and how they may affect prominence.
+Interestingly, the trend of western individuals being more notable does *not* continue when looking at already notable people (as shown by the lower predicted prominence of those from Oceania deemed to be part of the Western world).
+Even though the model underestimates the spread of the data (as mentioned later-on in @sec-weaknesses , it is evident that those from Eastern Asia overall have a higher prominence on Wikipedia.
 
-Interestingly, the trend of western individuals being more notable does *not* continue when looking at already notable people (as shown by the lower predicted prominence of those from Oceania deemed to be part of the Western world).
-Even though the model underestimates the spread of the data, it is evident that those from Eastern Asia are an outlier in terms of prominence.
+Furthermore, the large range associated with the majority of subregions suggests that an individuals subregion, overall, does not tend to be too significant of a predictor variable.
+Nearly every subregion, other than a few, contain a confidence interval that includes 0 (suggesting a notable chance that the difference may be negligible).
+
+Larger ranges in confidence intervals also directly correlate to how much available data there is on the specific subregion, such as the large confidence interval range from Oceania (not including Australia/New Zealand).
+This comes as no surprise, as the dataset has the lowest proportion of notable individuals out of any subgroup (as shown by @sec-subregion in the data section).
 
@@
 
-some studies, including the one by [@Banaji_Greenwald], highlighted that unconscious gender stereotyping was present and that individuals assigned a higher assignment of fame to males than females.
+Some studies, including the one by [@Banaji_Greenwald], highlighted that unconscious gender stereotyping was present and that individuals assigned a higher assignment of fame to males than females.
 Another meta-analysis of gender inequality in the workplace by [@workplace_sexism] highlights sexism where women tend to receive less promotions and less leadership roles, among other factors.
 Women receiving less leadership and more lower-status roles in the workplace could easily translate into biases in societal prominence.
+The proportion of notable men compared to women, as shown in @sec-analysis-of-variables, reflects this bias - with men being very much overrepresented in this dataset.
 
-However, the findings of this study do not entirely confirm previous studies between the relationship of gender and fame (which is heavily associated with prominence).
-In fact, the results relating to gender (shown in [@fig-gender_prediction]) highlight that notable women tend to be slightly more prominent than notable men.
-However, it also suggests that there is a large amount of variation in prominence  between notable men and women, indicating that gender is likely not a significant characteristic in predicting prominence from those who are already notable.
+However, when focusing exclusively on those who are already notable, the findings of this paper do not support previous studies regarding the relationship of gender on prominence.
+In fact, the results relating to gender (shown in [@fig-gender_prediction]) highlight that notable women tend to be slightly more prominent than notable men - although not by much.
+It also suggests that there is a large amount of variation in prominence between notable men and women, indicating that gender is likely not a significant characteristic in predicting prominence from those who are already notable.
+The insignificance of the `gender` variable is supported by the results in `modelsummary()` which indicate a very small positive difference in prominence with being a male, but with a very large p-value (suggesting that this difference could very well be due to chance).
 
-It also may be possible that the underrepresentation of women in this dataset means that the women who are already notable require a higher threshold of prominence to be on the dataset in the first place.Future studies can be conducted to explore the relationship between already notable people and how gender may (or may not) be associated with prominence.
+It also may be possible that the underrepresentation of women in this dataset means that the women who are already notable require a higher threshold of prominence to be on the dataset in the first place.
+Future studies can be conducted to explore the relationship between already notable people and how gender may (or may not) be associated with prominence.
+
+## Prominence by Occupation/Domain of Influence {#sec-prominence-by-occupation}
+
+Prominence tends to be strongly associated with an individuals occupation, as shown by @fig-occupation_results and @tbl-modelresults.
+In fact, the difference based on occupation is so large that the groups with most prominence (such as "culture-core" or "family") are, on average, 30 percentile points more prominent than those with a category of "missing" (as shown in @fig-occupation_results).
+Unsurprisingly, those with "missing" occupations tend to be much less prominent overall.
+It is quite intuitive that a lack of information on an individual correlates to lower overall prominence.
+Additionally, like other variables, `occupation` conserves the same trend of more popular categories having a more accurate model prediction.
+
+Furthermore, the overall prominence based on occupation may correlate to the exclusivity of the respective occupation/group.
+For example, those belonging to 'nobility' or 'family' may tend to be more prominent as belonging to the noble class or belonging to a powerful family is inherently a very small and elite group of people.
+This could be compared to a less prominent occupation, such as "Worker/Business(small)", which often includes those who are farmers, librarians, or booksellers - a much less elite occupation.
 
@@
 The results from the `modelsummary()`, which summarize the model, are shown in [@tbl-modelresults].
-Unsurprisingly, those that do not have their occupations mentioned (`occupationMissing` in `modelsummary()`) tend to be much less prominent overall.
-It is quite intuitive that a lack of information on an individual correlates to lower overall prominence.
+As mentioned in @sec-prominence-by-occupation, it makes intuitive sense that an occupation of "missing" would correspond to a very large overall decrease in prominence.
 
-Interestingly, some occupations such as being involved in politics; being an important person in a large business; and being associated with sports or games also tend to have a notable effect on percentiles of prominence.  The results suggest that occupation plays quite an important role in determining prominence, at least compared to the other predictor variables.
-Additionally, those born in the time period from 1501-1700 AD and those from Central America tend to have a lower prominence.
-Future analyses could be done to explore whether there is genuinely a strong effect of these certain characteristics on prominence, as this also may indicate a potential flaw in the model.
+Interestingly, some occupations such as being involved in the military; being a politician; and being associated with administration/law also tend to have a notable effect on percentiles of prominence.
+The results suggest that occupation plays quite an important role in determining prominence, at least compared to the other predictor variables.
+Additionally, those born in the time period from 1501-1700 AD, 1501-1750AD, and 1901-2020 AD tend to have a much lower amount of prominence than those born before 500 AD (as mentioned in @sec-time-period-prominence).
 
-## Weaknesses
+## Weaknesses {#sec-weaknesses}
 
-### Results only relevant for those already considered "notable"
+### Results Only Relevant for Those Already Considered "Notable"
 
-analyses only takes into account people who are ALREADY PROMINENT.
-\@sec-analysis-of-variables identifies characteristics of prominent people, and the appearance of bias in favour of certain characteristics (such as being a man or from Western Europe) is already reflected.
+The correlations found in this paper only take into account people who are ALREADY already prominent.
+\[@sec-analysis-of-variables identifies characteristics of prominent people, and the appearance of bias in favour of certain characteristics (such as being a man or from Western Europe) is already reflected.
 However, since this study measures difference in prominence between those who are **already** notable, the linear model does not tend to highlight those biases as strongly.
+This is why, for example, being a male was not significantly correlated with prominence.
 
-### Unequal Distribution of Characteristics
+### Unequal Prevalence of Characteristics Affects Model Prediction
+
+Those with characteristics that are underrepresented in the dataset tend to have less accurate predictions of popularity from the model.
+This is mentioned in the model section (@sec-model-limitations) but has downstream consequences for the results, especially when analysing less represented subregions or occupation.
 
 Not only has the world population grown exponentially in the past few hundred years, but records of notable people can be lost due to time.
-This can make predictions of prominence heavily biased towards individuals who live (or have lived) in more recent time periods.
-It may be difficult to extend the finding of prominence onto individuals with less represented characteristics (including being born before 500AD).
+This can make the number of prominent individuals heavily biased towards individuals who live (or have lived) in more recent time periods.
+It may be difficult to extend the finding of prominence onto individuals with less represented characteristics (such as being born before 500AD).
+
+This also extends to occupations, as highlighted in @fig-occupation_results.
+The difference between the prediction of the model and the actual percentile rank are heavily correlated with the distribution of occupations (as shown in @fig-occupation_count).
+Limited entries of certain occupations, such as "other", "missing", and "family" tend to show a less accurate model prediction.
 
@@
 
-From \@fig-percentile_prediction, we can see the predictive ability of the model leaves a lot to be desired.
+From @fig-percentile_prediction, we can see the predictive ability of the model leaves a lot to be desired.
 It suggests that given the specific predictors of the model (related to gender, subregion, age, and broad categorization of occupation), there is still a lot of variability of prominence that is not explained by these predictors.
-This is further evident by the RMSE and R\^2 values shown in \@tbl-modelresults.
-The R\^2 value of 0.138 suggests that these predictors only explain 14% of the variance in `percentile_rank`, which is quite low.
+This is further evident by the RMSE and R\^2 values shown in @tbl-modelresults.
+The R\^2 value of 0.121 suggests that these predictors only explain around 12% of the variance in `percentile_rank`, which is quite low.
 This suggests that an individuals prominence on Wikipedia is largely explained by other factors not included in the model (including ones that are not measured in the original dataset).
@@
 We can also see that the model tends to put most of its predictions near the 50th-percentile mark.
-A more ideal model would have a more spread out prediction of percentile. This results in the model underestimating the overall spread/variance of the data, making some differences appear more stark than others.
-This phenomenon is also evident in figures that portray prediction results for given characteristics (such as \@fig-subregion_prediction, \@fig-time_period_prediction, and \@fig-gender_prediction).
+A more ideal model would have a more spread out prediction of percentile.
+This results in the model underestimating the overall spread/variance of the data, making some differences appear more stark than others.
+This phenomenon is also evident in figures that portray prediction results for given characteristics (such as @fig-subregion_prediction, @fig-time_period_prediction, and @fig-gender_prediction).
 This means that the model largely underestimates the overall spread/variance of the data, resulting in characteristic-related differences appearing more significant than they actually are.
 
-although the predictive ability of this model leaves room for improvement, the model is still quite useful for analysing overall trends of prominence for specific characteristics.
+Although the predictive ability of this model leaves room for improvement, the model is still quite useful for analysing overall trends of prominence for specific characteristics.
 
@@
 
-# Additional data details
+# Model details {#sec-model-details}
 
-# Model details {#sec-model-details}
+A final model was intended to be chosen after performing numerous tests on a full model. The full model was as follows:
+
+\begin{align}
+\text{prominence percentile} = &\ \beta_0 + \beta_1 \cdot \text{occupation} + \beta_2 \cdot \text{subregion} + \beta_3 \cdot \text{time period} \\
+&+ \beta_4 \cdot \log(\text{age}) + \beta_5 \cdot \text{gender} + \beta_6 \cdot (\text{time period} \times \log(\text{age})) \\
+&+ \beta_7 \cdot (\text{occupation} \cdot \text{gender}) + \epsilon
+\end{align}
+
+with the variables representing the following:
+
+-   $\beta_0$ : the intercept term when all other predictors are set to zero.
+-   $\beta_1$ : the effect of ones occupation (relative to one with an occupation of an Academic) on prominence percentile ranking.
+-   $\beta_2$ : the effect of ones geographical subregion (relative to the Caribbean) on prominence percentile ranking.
+-   $\beta_3$ : the effect of ones time-period (relative to those born before 500AD) on prominence percentile ranking
+-   $\beta_4$ : the logarithmic effect of age (`years_since_birth`).
+-   $\beta_5$ : The effect of ones gender (relative to female) on prominence percentile ranking
+-   $\beta_6$ : the interaction between the individuals time period (at birth) and age
+-   $\beta_7$ : the interaction between ones occupation and their gender
+-   $\epsilon$ : residual term, or the variation in percentile_ranking not due to the predictors.
+
+The large amount of variables an interaction terms highlights the associations between different predictors, with their relationships being shown in @sec-data-cleaning-and-variables.
+The ultimate motive for starting with a large model was to include the possibility of numerous different predictor variables being important for prediction.
+However, the final model was eventually chosen after a series of numerous statistical tests (including BIC, VIF, and RMSE).
 
@@
 
+The method of BIC was an important tool used to remove unnecessary terms, and was the first step for obtaining the full model.
+This was preferred over a similar method called the Akaike information criterion, since the BIC is more harsh with an overly complex model (increasing the chance of possibly insignificant interaction terms being removed).
+BIC was performed with a backwards selection process (that goes from a more complex to less complex model) and removed the terms `gender` and `gender:occupation` (an interaction term).
+The BIC helped with the decision to remove the gender/occupation interaction variable, but the `gender` variable was still retained to further analyse its significance in prominence.
+
+## Variance Inflation Factor (VIF) {#sec-vif}
+
+VIF is a technique that is used to help address the linear regression assumption of multicollinearity (that is, correlations between different predictor variables).
+More specifically, it shows how much variance of an estimated regression coefficient increases due to multicollinearity.
+Higher GVIF values indicate potential issues with multicollinearity that could obstruct how significant a characteristic truly is.
+With the help of the `car` package (@car), the VIF table of the updated model (with `gender:occupation` removed) is shown in @tbl-vif.
+
+```{r}
+#| label: tbl-vif
+#| tbl-cap: GVIF Values (and thus multicollinearity) High in Time-Related Predictors
+#| echo: false
+#| warning: false
+
+new_model <- lm(data=training_data, percentile_rank ~ occupation + subregion + time_period + log(years_since_birth) + 
+                        gender + time_period:log(years_since_birth))
+vif <- car::vif(new_model)
+kable(vif)
+```
+
+The high GVIF shown by `time_period` and `log(years_since_birth)` is expected as they both relate to an individuals time of birth.
+However, the decision to remove `log(years_since_birth)` was to see more directly how time period influenced prominence.
+This aided with the discovery that the time period has quite a significant result on prominence, as shown in @tbl-modelresults.
+
 ## RMSE Comparison {#sec-rmse-comparison}
 
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
+After obtaining a reduced model, the root mean squared error (RMSE) between different models was used to verify that the reduced model still retained predictive abilities.
+RMSE calculations were performed with the help of the MLmetrics (@MLmetrics)
 
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
+```{r}
+#| label: tbl-rmse
+#| tbl-cap: Similar RMSE highlights Relatively Similar Predictive Ability Between Reduced and Full Model
+#| echo: false
+#| warning: false
 
-`{# {r} # plot(relevance_model, "trace") #  # plot(relevance_model, "rhat")`
+full_model <- lm(data=training_data, percentile_rank ~ occupation + subregion + time_period + log(years_since_birth) + 
+                        gender + time_period:log(years_since_birth) + gender:occupation)
 
-<!-- ```{r} -->
+reduced_model = BIC_model
+pred1 = predict(full_model, testing_data)
+pred2 = predict(reduced_model, testing_data)
 
-<!-- #| eval: true -->
+rmse_full = RMSE(pred1, testing_data$percentile_rank)
+rmse_reduced = RMSE(pred2, testing_data$percentile_rank)
 
-<!-- #| echo: false -->
+rmse_table <- data.frame(
+  Model = c("RMSE for Reduced Model", "RMSE for Full Model"),
+  RMSE = c(rmse_reduced, rmse_full)
+)
 
-<!-- #| message: false -->
+kable(rmse_table, col.names = c("Model", "Root Mean Square Error"))
+```
 
-<!-- #| warning: false -->
+A nearly identical root mean square error suggests that the reduced model is roughly as good as the full model when it comes to predicted vs.
+actual values.
+This comes at the benefit of having less multicollinearity and having a less complex model.
+Thus, the reduced model was ultimately chosen.
 
-<!-- #| label: fig-ppcheckandposteriorvsprior -->
+## Full modelsummary() Results
 
-<!-- #| layout-ncol: 2 -->
+Previous summaries of the final model focused more on a handful of significant variables.
+However, @tbl-full-modelsummary-results provides each characteristic and its influence on prominence of notable people.
+The table was generated with the help of the `kableExtra` package (@kableExtra).
 
-<!-- #| fig-cap: "Examining how the model fits, and is affected by, the data" -->
+```{r, fig.width=8, fig.height = 30}
+#| label: tbl-full-modelsummary-results
+#| tbl-cap: Full Results of the Model, Including Characteristics Not Strongly Associated With Wikipedia Prominence
+#| echo: false
+#| warning: false
 
-<!-- #| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"] -->
+library(kableExtra)
 
-<!-- pp_check(first_model) + -->
+model_summary= modelsummary(BIC_model, output = "default")
 
-<!--   theme_classic() + -->
-
-<!--   theme(legend.position = "bottom") -->
-
-<!-- posterior_vs_prior(first_model) + -->
-
-<!--   theme_minimal() + -->
-
-<!--   scale_color_brewer(palette = "Set1") + -->
-
-<!--   theme(legend.position = "bottom") + -->
-
-<!--   coord_flip() -->
-
-<!-- ``` -->
-
-<!-- ## Diagnostics -->
-
-<!-- @fig-stanareyouokay-1 is a trace plot. It shows... This suggests... -->
-
-<!-- @fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests... -->
-
-<!-- # ```{r} -->
-
-<!-- # #| echo: false -->
-
-<!-- # #| eval: true -->
-
-<!-- # #| message: false -->
-
-<!-- # #| warning: false -->
-
-<!-- # #| label: fig-stanareyouokay -->
-
-<!-- # #| fig-cap: "Checking the convergence of the MCMC algorithm" -->
-
-<!-- # #| fig-subcap: ["Trace plot", "Rhat plot"] -->
-
-<!-- # #| layout-ncol: 2 -->
-
-<!-- # -->
-
-<!-- # plot(first_model, "trace") -->
-
-<!-- # -->
-
-<!-- # plot(first_model, "rhat") -->
-
-<!-- # ``` -->
-
-<!-- # -->
+model_summary
+```
 
@@
 Data is also extracted from Wikidata, which contains structured data linked to a Wikipedia page.
-The sample of individuals chosen was defined by this data (The researchers then merged the information on both websites to avoid dealing with duplicates and ensure data reliability.
+The sample of individuals chosen was defined by this data (the researchers then merged the information on both websites to avoid dealing with duplicates and ensure data reliability).
 
@@
 #| echo: false
+#| warning: false
 
-variable_names <- colnames(raw_data)
+variable_names <- c("wikidata_code", "birth", "death", "updated_death_date", 
+                    "approx_birth", "approx_death", "birth_min", "birth_max", 
+                    "death_min", "death_max", "gender", "level1_main_occ", 
+                    "name", "un_subregion", "birth_estimation", "death_estimation", 
+                    "bigperiod_birth_graph_b", "bigperiod_death_graph_b", "curid", 
+                    "level2_main_occ", "freq_main_occ", "freq_second_occ", 
+                    "level2_second_occ", "level3_main_occ", "bigperiod_birth", 
+                    "bigperiod_death", "wiki_readers_2015_2018", "non_missing_score", 
+                    "total_count_words_b", "number_wiki_editions", "total_noccur_links_b", 
+                    "sum_visib_ln_5criteria", "ranking_visib_5criteria", "all_geography_groups", 
+                    "string_citizenship_raw_d", "citizenship_1_b", "citizenship_2_b", 
+                    "list_areas_of_rattach", "area1_of_rattachment", "area2_of_rattachment", 
+                    "list_wikipedia_editions", "un_region", "group_wikipedia_editions", 
+                    "bplo1", "dplo1", "bpla1", "dpla1", "pantheon_1", "level3_all_occ")
 
@@
 
-## Potential Enhancements for Measuring Prominence
+-   Western-centric bias: the researchers focused specifically on 7 popular Wikipedia languages, which are predominantly spoken by those in the West.
+Additionally, 30% of individuals in the dataset come from English Wikipedia, which skews the data towards Western countries.
 
-###
+-   Gender-bias: Strong evidence of unequal gender representation exists in terms of notable people on Wikipedia.
+Although this bias of Wikipedia is not a fault of the researchers, this gender bias results in comparatively less extrapolation of dataset trends compared to men.
 
-###
+-   Bias towards those who have internet access: the nature of obtaining notable people through an online encyclopedia, such as Wikipedia, likely may not include notable people in communities that do not have the same level of internet access.
+This is especially a concern in countries that do not have widespread internet usage.
+
+-   Recency-bias: Individuals who are from more modern time periods benefit from much more documentation and representation.
+
+## Potential Enhancements for Dataset
+
+Although Wikipedia can give an idea on the overall trends relating to prominence, the limitations of this dataset have consequences for predicting prominence more generally.
+There are, however, some ways this can potentially be mediated.
+Not only do these improvements improve the ability to make inferences on prominence, but they also provide a more robust dataset.
+This improvements may include:\
+
+-   including data from historical records or repositories that are more focused on women to address their under representation.
+An intentional effort to select women could mitigate the bias against them.
+
+-   including non-European langauges in order to gain a more comprehensive dataset of notable people that exist.
+This could also include cooperating with historians or figures that are knowledgeable on notable figures (which may not be included on Wikipedia).
+
+-   more comprehensive measures of prominence that do not just take in Wikipedia-related metrics.
+This may include interviews with experts, as well as social media mentions (for more modern figures) to compare overall prominence.
 

### 2024-12-04 scripts/00-simulate_data.R

@@ -1,52 +1,65 @@
 #### Preamble ####
-# Purpose: Simulates a dataset of Australian electoral divisions, including the 
-  #state and party that won each division.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
+# Purpose: Simulates a fictitious dataset of 50 Notable People
+# Author: Parth Samant
+# Date: 01 December 2024
+# Contact: parth.samant@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: The `tidyverse` package must be installed
-# Any other information needed? Make sure you are in the `starter_folder` rproj
+# Pre-requisites: The `tidyverse` and `arrow` package must be installed
 
 
 #### Workspace setup ####
 library(tidyverse)
+library(arrow)
 set.seed(853)
 
 
-#### Simulate data ####
-# State names
-states <- c(
-  "New South Wales",
-  "Victoria",
-  "Queensland",
-  "South Australia",
-  "Western Australia",
-  "Tasmania",
-  "Northern Territory",
-  "Australian Capital Territory"
+#### Simulates data ####
+n <- 50
+
+occupation_names <- c(
+  "Culture-core", "Academia", "Sports/Games", "Politics", "Military",
+  "Administration/Law", "Corporate/Executive/Business (large)",
+  "Culture-periphery", "Religious", "Explorer/Inventor/Developer",
+  "Worker/Business (small)", "Family", "Nobility", "Other", "Missing"
 )
 
-# Political parties
-parties <- c("Labor", "Liberal", "Greens", "National", "Other")
-
-# Create a dataset by randomly assigning states and parties to divisions
-analysis_data <- tibble(
-  division = paste("Division", 1:151),  # Add "Division" to make it a character
-  state = sample(
-    states,
-    size = 151,
-    replace = TRUE,
-    prob = c(0.25, 0.25, 0.15, 0.1, 0.1, 0.1, 0.025, 0.025) # Rough state population distribution
-  ),
-  party = sample(
-    parties,
-    size = 151,
-    replace = TRUE,
-    prob = c(0.40, 0.40, 0.05, 0.1, 0.05) # Rough party distribution
-  )
+subregion_names <- c(
+  "Western Europe", "Northern America", "Southern Europe", "Eastern Europe",
+  "Oceania Western World", "Eastern Asia", "Central America", "West Africa",
[…]

### 2024-12-04 scripts/01-test_simulated_data.R

@@ -1,89 +1,114 @@
 #### Preamble ####
-# Purpose: Tests the structure and validity of the simulated Australian 
-  #electoral divisions dataset.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
+# Purpose: Tests the structure and validity of the simulated Notable People Dataset
+# Author: Parth Samant
+# Date: 01 December 2024
+# Contact: parth.samant@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: 
-  # - The `tidyverse` package must be installed and loaded
-  # - 00-simulate_data.R must have been run
-# Any other information needed? Make sure you are in the `starter_folder` rproj
+# Pre-requisites:
+# - The `tidyverse`, `arrow`, and `testthat` package must be installed
+# - 00-simulate_data.R must have been run
 
 
 #### Workspace setup ####
+library(testthat)
 library(tidyverse)
+library(arrow)
 
-analysis_data <- read_csv("data/00-simulated_data/simulated_data.csv")
+simulated_data <- read_csv("data/simulated_data/simulated_data.csv")
 
+
+occupation_names <- c(
+  "Culture-core", "Academia", "Sports/Games", "Politics", "Military",
+  "Administration/Law", "Corporate/Executive/Business (large)",
+  "Culture-periphery", "Religious", "Explorer/Inventor/Developer",
+  "Worker/Business (small)", "Family", "Nobility", "Other", "Missing"
+)
+
+subregion_names <- c(
+  "Western Europe", "Northern America", "Southern Europe", "Eastern Europe",
+  "Oceania Western World", "Eastern Asia", "Central America", "West Africa",
+  "South Asia incl. Indian Peninsula", "South America", "North Africa",
+  "Caribbean", "Northern Europe", "Central Africa",
+  "Western Asia (Middle East Caucasus)", "East Africa", "Southern Africa",
+  "SouthEast Asia", "Central Asia", "Oceania not Aus Nze"
+)
+
+time_period_names <- c("5. 1901-2020AD", "4. 1751-1900AD", "3. 1501-1750AD", "2. 501-1500AD", "1. Before 500AD")
+
+#### Test Data ####
 # Test if the data was successfully loaded
-if (exists("analysis_data")) {
+if (exists("simulated_data")) {
   message("Test Passed: The dataset was successfully loaded.")
 } else {
   stop("Test Failed: The dataset could not be loaded.")
 }
 
[…]

### 2024-12-04 scripts/03-clean_data.R

@@ -19,17 +19,36 @@ raw_data <- read_csv("data/raw_data/raw_data.csv")
 # To make data reproducible
 set.seed(201)
 
+# raw_data$ranked_visib <- rank(raw_data$ranking_visib_5criteria, ties.method = "average")
+# 
+# # Step 2: Scale ranks to [0, 1]
+# n <- nrow(raw_data)  # Number of observations
+# raw_data$scaled_ranks <- (raw_data$ranked_visib - 0.5) / n
+# 
+# # Step 3: Apply the inverse normal transformation
+# # This maps scaled ranks to the quantiles of a standard normal distribution
+# raw_data$normal_transformed <- qnorm(raw_data$scaled_ranks)
+# 
+# # Step 4: (Optional) Center and scale to ensure standard normal
+# # Not usually needed since qnorm already produces standard normal values
+# raw_data$standard_normal <- scale(raw_data$normal_transformed)
+
 
 #Selecting for relevant columns, as well as making a couple new ones
 cleaned_data <- raw_data |>
   mutate(
     percentile_rank = percent_rank(-ranking_visib_5criteria),
     years_since_birth = 2024-birth
-    ) |>
+  ) |>
   select(years_since_birth, gender, level2_main_occ, bigperiod_birth_graph_b, un_subregion, percentile_rank) |> 
-  filter(gender %in% c("Male", "Female"),
-    if_all(c(years_since_birth, gender, level2_main_occ, bigperiod_birth_graph_b, un_subregion, percentile_rank), ~ !is.na(.))) |>
-  # sample_n(20000, replace = FALSE) |>
+  filter(!is.na(years_since_birth) &
+           !is.na(gender) &
+           !is.na(level2_main_occ) &
+           !is.na(bigperiod_birth_graph_b) &
+           !is.na(un_subregion),
+         gender %in% c("Male", "Female"),
+         ) |>
+  sample_n(20000, replace = FALSE) |>
   rename(
     occupation = level2_main_occ,
     time_period = bigperiod_birth_graph_b,
@@ -48,13 +67,21 @@ cleaned_data <- raw_data |>
       )
   )
 
+#### Removing incorrectly labeled time periods ####
 
-# Filter and sample 1000 entries for each time period
-# sampled_data <- cleaned_data |>
[…]

### 2024-12-04 scripts/04-test_analysis_data.R

@@ -1,69 +1,67 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 26 September 2024 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Tests the structure and validity of the Notable People Dataset
+# Author: Parth Samant
+# Date: 01 December 2024
+# Contact: parth.samant@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
 
 
 #### Workspace setup ####
 library(tidyverse)
 library(testthat)
 
-data <- read_csv("data/02-analysis_data/analysis_data.csv")
+data <- read_parquet("data/analysis_data/analysis_data.parquet")
 
 
-#### Test data ####
-# Test that the dataset has 151 rows - there are 151 divisions in Australia
-test_that("dataset has 151 rows", {
-  expect_equal(nrow(analysis_data), 151)
+#### Test Data ####
+if (exists("data")) {
+  message("Test Passed: The dataset was successfully loaded.")
+} else {
+  stop("Test Failed: The dataset could not be loaded.")
+}
+
+# Check if any column contains NA values
+test_that("No NA values in the dataset", {
+  expect_false(any(is.na(data)), info = "Dataset contains NA values")
 })
 
-# Test that the dataset has 3 columns
-test_that("dataset has 3 columns", {
-  expect_equal(ncol(analysis_data), 3)
+# Check if no negative values of years since birth
+test_that("Years Since Birth are all positive", {
+  expect_true(all(data$years_since_birth > 0), info = "Dataset contains negative years_since_birth entries")
 })
 
-# Test that the 'division' column is character type
-test_that("'division' is character", {
-  expect_type(analysis_data$division, "character")
+# Tests if years_since_birth correctly corresponds to the time period of birth
+test_that("Time Period and Years since birth variable in agreement", {
+  get_time_period <- function(year_of_birth) {
+    if (year_of_birth >= 1901) return("5. 1901-2020AD")
+    if (year_of_birth >= 1751) return("4. 1751-1900AD")
+    if (year_of_birth >= 1501) return("3. 1501-1750AD")
+    if (year_of_birth >= 501)  return("2. 501-1500AD")
+    return("1. Before 500AD")
+  }
[…]

### 2024-12-04 scripts/05-exploratory_data_analysis.R

@@ -1,37 +1,74 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Conducts Exploratory Data Analysis on Notable People Dataset
+# Author: Parth Samant
+# Date: 01 December 2024
+# Contact: parth.samant@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites:
+# - The `tidyverse` and `arrow` package must be installed
 
 
 #### Workspace setup ####
 library(tidyverse)
-library(rstanarm)
+library(arrow)
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
-
-### Model data ####
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
-  )
+cleaned_data <- read_parquet("data/analysis_data/analysis_data.parquet")
 
 
-#### Save model ####
-saveRDS(
-  first_model,
-  file = "models/first_model.rds"
-)
+# Summary statistics on cleaned data
+summary(cleaned_data)
+
+# Plotting histograms of characteristics
+ggplot(cleaned_data, aes(x = occupation)) +
+  geom_bar(fill = "skyblue", color = "black") +
+  labs(x = "Occupation", y = "Count") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+ggplot(cleaned_data, aes(x = time_period)) +
+  geom_bar(fill = "darkred", color = "black") +
+  labs(x = "Time Period", y = "Count") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+ggplot(cleaned_data, aes(x = subregion)) +
+  geom_bar(fill = "purple", color = "black") +
+  labs(x = "Subregion", y = "Count") +
[…]

### 2024-12-04 scripts/06-model_data.R

@@ -1,19 +1,18 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Models Prominence of Notable People and Performs Statistical Tests
+# Author: Parth Samant
+# Date: 25 November 2024
+# Contact: parth.samant@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Any other information needed? None
 
 
 #### Workspace setup ####
 library(tidyverse)
-library(rstanarm)
 library(MLmetrics)
-library(tidymodels)
 library(broom)
+library(tidymodels)
 
 
 #### Read data ####
@@ -26,11 +25,9 @@ analysis_data <- analysis_data |>
     subregion = factor(subregion),
     time_period = factor(time_period)
   )
-  
+
 # To make data reproducible
 set.seed(200)
-
-#formula = percentile_rank ~  subregion + log(years_since_birth) * time_period + gender + occupation,
 
 
 ### Training and Test Split ###
@@ -39,32 +36,20 @@ split <- initial_split(analysis_data, prop = 0.7)
 training_data <- training(split)
 testing_data <- testing(split)
 
-### Model data ####
-relevance_model <- stan_glm(
-  percentile_rank ~  occupation + subregion + years_since_birth + 
-    gender + occupation:gender,  # Interaction as fixed effect
-  data = training_data,
-  family = gaussian(),
-  prior = normal(0, 1),
-  prior_intercept = normal(0.5, 1),
-  cores = 4
+### Model informed by BIC ###
+
+relevance_model <- lm(data = training_data, percentile_rank ~ occupation + subregion + time_period + log(years_since_birth) +
+  gender + time_period:log(years_since_birth) + gender:occupation)
+
+n <- nrow(training_data)
+stepfit <- stats::step(relevance_model,
+  direction = "backward",
+  k = log(n)
 )
 
 
-### Model informed by BIC ###
-
-relevance_model <- lm(data = training_data, percentile_rank ~  occupation + subregion + time_period + log(years_since_birth) + 
[…]

### 2024-12-04 paper/paper.qmd
updated paper

@@
 title: "Analyzing Trends on the Characteristics of Notable People on Wikipedia"
-subtitle: "[BLAH, BLAH,BLAH] characteristics are associated with increased prominence"
+subtitle: "an Individuals Time Period and Occupation Strongly Associated with Prominence"
 author: 
@@
 In this paper, I analyzed a dataset of notable people on Wikipedia from 3500 BCE to 2018 AD to identify whether certain characteristics (such as age and gender) were correlated with prominence.
-The analysis found that [WHAT DID YOU FIND???].
-The findings highlight...."
+The analysis found that occupation and time period were most strongly associated with prominence, with subregion and gender being less significant.
+This highlights how prominence between already notable people selects for different characteristics."
 format: pdf

### 2024-12-14 scripts/02-download_data.R
Update 02-download_data.R

@@ -5,7 +5,6 @@
 # Contact: parth.samant@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: Make sure tidyverse, readr, httr, R.utils libraries have been downloaded
-# Any other information needed? None
 
 
 #### Workspace setup ####

### 2024-12-14 scripts/03-clean_data.R
Update 03-clean_data.R

@@ -5,8 +5,6 @@
 # Contact: parth.samant@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: Make sure tidyverse, readr, and arrow libraries have been downloaded
-# Any other information needed? None
-
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-12-14 scripts/06-model_data.R
Update 06-model_data.R

@@ -4,8 +4,7 @@
 # Date: 25 November 2024
 # Contact: parth.samant@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? None
+# Pre-requisites: Make sure tidyverse, MLmetrics, broom, and tidymodels packages have all been installed
 
 
 #### Workspace setup ####

### 2024-12-14 paper/paper.qmd
slightly updates paper, adds .gitignore

@@
 title: "Analyzing Trends on the Characteristics of Notable People on Wikipedia"
-subtitle: "an Individuals Time Period and Occupation Strongly Associated with Prominence"
+subtitle: "Time Period and Occupation Strongly Associated with Individual Prominence"
 author: 
@@
 This encyclopedia provides information on a diverse range of topics from history to entertainment.
-
 Within this vast encyclopedia, there is also a collection of biographical information on "notable people" who have ever lived in the past few thousand years.
@@
 Those who were born in earlier time periods (such as before 500 BCE) were associated large increases in prominence.
-Additionally, those known for being part of a noble class, an important family, or for creative endeavors that shape culture (such as musicians, actors, or painters) also tend to have higher overall prominence.
-
-Subregion was somewhat associated with prominence, but with a large amount of variability.
+Additionally, those known for being part of a noble class, an important family, or for creative endeavors that shape culture (such as musicians, actors, or painters) also tend to have higher overall prominence.Subregion was somewhat associated with prominence, but with a large amount of variability.
 Notable individuals from Eastern Asia tend to have high levels of prominence, whereas those from Central America and Southern Africa have less.
-
-This paper also found that within those who are already prominent, gender tends to have a somewhat insignificant effect.
+It was also found that within those who are already prominent, gender tends to have a somewhat insignificant effect.
 

### 2024-12-14 paper/paper.qmd
rewording abstract of paper

@@
 In this paper, I analyzed a dataset of notable people on Wikipedia from 3500 BCE to 2018 AD to identify whether certain characteristics (such as age and gender) were correlated with prominence.
-The analysis found that occupation and time period were most strongly associated with prominence, with subregion and gender being less significant.
-This highlights how prominence between already notable people selects for different characteristics."
+The analysis found that occupation and time period were most strongly associated with prominence, with factors affecting prominence among already notable individuals differing from those that initially lead to notability.
+The findings highlight how biases against groups may be amplified or minimized when strictly analysing subgroups like notable individuals."
 format: pdf

### 2024-12-14 paper/paper.qmd
updates paper by making some graphs fit on page, updates model

@@
 
-```{r}
+```{r, out.width='70%', out.height='70%'}
 #| label: fig-time_period_prediction
@@
 ```
-
+\newpage
 @fig-time_period_prediction highlights the large variation in model predictions based on the time period the individual was born in.
@@
 
-\`\newpage
+\newpage
 
@@
 
-```{r, fig.width=8, fig.height = 30}
+```{r, tbl.width=1, tbl.height=5}
 #| label: tbl-full-modelsummary-results
@@
 
-model_summary= modelsummary(BIC_model, output = "default")
-
-model_summary
+# modelsummary(BIC_model, output = "default", table.font.size = 4)
+
+modelsummary(BIC_model, output = "kableExtra", statistics = NULL) |>
+    kable_styling(font_size = 8, full_width = FALSE, bootstrap_options = "striped", position = "center") |>
+    row_spec(0, bold = TRUE)
 ```
